### 2023-12-27 paper/paper.tex
initial commit

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={blue},
    citecolor={blue},
    urlcolor={blue}
}
\usepackage[natbib=true, style=numeric,sorting=none]{biblatex}
\addbibresource{bibliography.bib}
\usepackage[title]{appendix}

\title{Arbius: A Decentralized Machine Learning Network with Economic Incentive}
\author{Kasumi}
\date{October 2023}

\begin{document}

\maketitle

\section{Introduction}

A peer-to-peer hybrid proof-of-work/proof-of-stake token (AIUS) based on reproducible computation allows anyone in the world to serve and request AI models without requiring a trusted third party. Such a system is capable of producing results such as Stable Diffusion \cite{stablediffusion} image generation with low latency overhead and competitive fees to centralized providers. Models are able to accrue fees into smart contracts, providing a decentralized a way for creators to generate income from utility and usage of their work. Censoring models is economically infeasible, allowing for truly unstoppable AI systems.

\section{Tasks}

Tasks are the main interaction mechanism for the network. Tasks operate somewhat like a mix between a normal cryptocurrency transaction and the creation of a block, both deriving rewards and having an attached fee to send.

To create a task a user prepares input data for the task and submits a transaction containing the model and the input data. along with an optional fee (paid in AIUS) to the blockchain. The IPFS\cite{benet2014ipfs} Content Identifier (CID) is calculated by a smart contract and stored, miners may automatically mirror the input data.

As time goes on, the market will adjust what an appropriate fee is for different tasks. A fee market must emerge, as there is a real computational cost with generating data.

The flow for a standard task creation:

\begin{enumerate}
    \item User formats a task request
    \item User broadcasts a transaction calling createTask and attaches a fee
    \item Contract calculates CID of input data and stores it
    \item Solvers that are scanning for tasks download the request data
    \item Solvers run associated model using user's input and a seed derived from the task and system state
    \item Solvers pin model response to IPFS and broadcast a commitment transaction referencing the task and response hash
    \item Solvers broadcast a solution referencing the task, commitment, and solution data. The first solution proposed wins.
    \item The user is scanning for solutions to their task, and when they see one they can use the result immediately or wait for claim period to ensure other solvers did not contest.
    \item The winning solver waits for a period of time to allow for other solvers to contest the solution, prior to being able to claim the task fee and any task reward.
\end{enumerate}

Other solvers verify the solution is valid. If one disagrees they may initiate a contestation. A standard contestation flow looks like:

\begin{enumerate}
    \item Solver contests a solution referencing its task id
    \item Other solvers are scanning for new contestations, and choose to verify the task was completed accurately by the solution submitter
    \item Solvers vote over a period of time on whether the contestation was valid.
    \item When the voting period is finished, the winning voters receive the losing voters slashed funds, and the task submitter gets refund if solution submitter was determined to provide an inaccurate result.
\end{enumerate}

More details about contestations can be found in \ref{contestation}.

\subsection{Task Reward} \label{taskreward}

AIUS tokens are minted and rewarded to solvers on solution claiming, in addition to any fees paid by the task creator. The amount of the reward is determined by the time the claim is initiated multiplied by an exponential curve determined by the ratio of the real total supply of AIUS to the expected total supply of AIUS at the time of claiming. The larger the ratio of the real total supply to expected total supply, the lower the task reward will be.

Task rewards works similarly to how difficulty in Bitcoin \cite{bitcoin} adjusts the work required to mine a block to target an emission schedule, we adjust the reward amount per task to target our emission schedule(\ref{tokenomics} for schedule).

Task rewards can be enabled on a per model basis through the governance system.

\section{Models}

Machine learning models may be registered permissionlessly. Each model references a docker container which follows a standard Cog \cite{cog} interface for interacting with it. This allows great flexibility in the types of models that can be run, and importantly, allows each run to be reproducible.

A limitation of this design results in models with a low amount of supporting solvers being significantly more susceptible to 51\% attack. A signalling mechanism exists to help notify other participants in the network of self-reported supporting solvers.

Models can optionally have a flat-fee they charge for each use, which accrues in the models specified address. This allows models to operate as DAOs, with their own token dynamics decided by their respective teams. A simple case would be to have the fees accrued be distributed pro-rata to holders of the DAO.

A useful property of having the models operate as DAOs allows models to be sold in ICOs, or for teams to be able to divest ownership and trade model tokens on decentralized exchanges. Interesting and useful model tokens may have high speculative value due to their potential to accrue a large portion of fees over time.

There are no restrictions placed on the types of models that may be created and used on the network. It would be incredibly difficult or impossible to prevent or to shut down access to open models.

\section{Solvers}

Solvers scan for new tasks and decide if the associated fee plus task reward is profitable to attempt to solve for the estimated compute time and likelihood of providing the first solution.

Because winning high fee tasks results in greater income for the solver, solvers are more likely to take these tasks than lower fee tasks. However, because a task which has not been solved for some amount of time is less likely to be in the process of being solved by another solver, the expected chance of winning by providing the first solution to older tasks is greater. This dynamic encourages all tasks with an appropriate attached minimum fee to be completed in a reasonable amount of time.

Task hashes are combined with the previous task hash to create the task id. The task id used to generate the seed for running models deterministically with taking the modulo of the task id like $ h \mod \text{0x1FFFFFFFFFFFF0} $ This is $\approx 2^{53}$. Solvers must solve the task using the calculated seed so that other solvers can verify the solution, and so solvers which propose their own tasks cannot easily pre-generate solutions to tasks in order to farm for task rewards, ensuring other solvers have a chance to solve tasks as well.

Once complete, solvers upload the result to IPFS and save the CID. Then they submit a commitment containing a hash of their solution in order to prevent others from stealing their work by watching the mempool (or sequencer queue or similar). Once the commitment is confirmed, they can safely broadcast their transaction referencing the task and their solution CID. The task is now locked from others submitting.

\subsection{Contestation} \label{contestation}

When solvers see a solution submitted for a task they are working on or have finished, they should check the proposed solution's hash is equal to their result's hash. If it is not, the proposed solution may be contested. A solver can generate a contestation to any submitted solution which has not already been claimed. When a contestation is initiated, a vote for and against the contestation by the contester and the solver respectively is placed. Other solvers may vote on whether or not the contestation is valid. The losers of the vote have their staked balance slashed, and this balance is distributed to the winners of the vote.

The contester in a winning contestation would win 50\% of the slashed total, with the other voters in agreement receiving share of the remaining 50\%. The user who requested the task would have their fees refunded, and no task reward would be issued.

If a contestation is made and the vote fails to gain majority, the contester (and any other solvers who voted with them) would be slashed, and the original solver would receive 50\% of the slashed rewards, with the other solvers who voted correctly receiving the other 50\%, and the original solver would receive the associated fee for the task and the task reward.

Because the potential income for resolving a dispute is much higher than a normal task, other solvers have a financial incentive to participate in the voting and validation scheme. As long as more than 50\% of the solvers are honest, it is a losing proposition to submit invalid solutions to tasks, or to contest valid solutions. Due to the large reward possible for finding solvers who are providing invalid solutions and being the first to contest, solvers have a shared interest in finding bad-acting solvers and eliminating them from the network.

The contestation mechanism, revolving around reproducible off-chain computation, is why a ``proof-of-stake'' voting element must be injected into the system.

\section{Tokenomics} \label{tokenomics}

AIUS has 1 million max supply, with a time based target total supply of $1000000(1-{0.5^{y})}$ where y is year. After 1 year, there should be approximately 500k tokens minted, and after 2 years approximately 750k tokens minted. After 7 years approximately 99\% of tokens should be minted.

\begin{figure}[H]
\includegraphics[width=8cm]{totalsupply}
\centering
\end{figure}

The real emission rate (recall \ref{taskreward}) will be slightly faster than the target emission rate, due to the variable task reward. However, it is unlikely to be much more than 10\% faster due to the exponential falloff of task rewards. 10\% greater total supply than expected total supply by time results in a 1024-fold reduction of task rewards.

10\% of all newly minted tokens, and 10\% of task fees are sent to the treasury. An additional 10\% of all newly minted tokens will be dripped to liquidity providers to incentivize AIUS/ETH liquidity; governance can adjust this percentage.

There are at least 4 ways for participants to earn with the AIUS protocol:

\begin{enumerate}
    \item Register a model and earn usage fees
    \item Solve tasks and earn task rewards and fees
    \item Stake AIUS and delegate to solver for portion of task rewards
    \item Stake AIUS/ETH LP tokens for portion of newly created AIUS
\end{enumerate}

\section{Governance}

All contracts and treasury are owned by a governor contract which implements Bravo \cite{bravo} style voting. An initial quorum requirement of 4\%, a 1 day voting delay for proposals, and 1 week voting period are set as the initial parameters. These and all other parameters and upgrades can be voted upon by the token holders.

The role of the treasury is to use the accrued tokens to promote and ensure open access to AI is preserved, using this and potential future technology to do so.

\section{Blockchain}

We choose Arbitrum Nova \cite{arbitrumnitro}. Arbitrum Nova is a Layer 2 optimistic rollup built on top of Ethereum. Nova has near-instant confirmation times, greatly reduced gas fees, and is the most decentralized given our low fee requirement.

We chose Nova over Arbitrum One to further reduce fees as the microtransactional nature of tasks and voting require consistently low overhead costs. Network participants should be comfortable using Arbitrum Nova without worrying about censorship.

\section{Conclusion}

We have proposed a system which allows for decentralized coordination of reproducible compute tasks, specifically those in machine learning. This system allows for proof-of-work based reward distribution, even when verifying the proof is as much work as generating it. By introducing an economically incentivized slashing system that encourages verification of reproducible computation, we ensure honesty of participants, as long as the majority of participants in the network are honest. Solvers have an incentive to not collude and attack the system as it would be against their own economic interests, reducing the threat of a sustained 51\% attack. The design is robust and simple, and allows other contracts and autonomous intelligent agents to interact with it.

\printbibliography

\newpage

\begin{appendices}

\section{Potential Use Cases}

\subsection{NFT Mint}

As an example of a contract integrating this system, imagine a NFT minting contract. The contract would store the system address and each claiming could trigger a task generation for a specific request input, such as for a beach themed art collection. The NFT contract would be able to reference the solutions CID for showing the image, and buyers of the NFT would have on-chain proof it was generated using specific model version and parameters.

\subsection{Parameter Competition}

An on-chain competition could be created with a goal to create a certain type of content. Participants would interact with a competition contract by providing their submitted task ids using this system, and the winner could be chosen by the competition creator. This could provide a cost effective way to design promotional content, films, or other sorts of media.

\subsection{Timestamped Proof of Work}

People interacting with autonomous agents may prefer to utilize text-to-speech and generated avatars so that they are more personable. Imagine you hire an autonomous consultant to help you with your project, and you provide payment for them to begin working. They may utilize this system, by creating hourly tasks to provide updates in video or audio form. If there was a need for arbitration in the future, the full history of timestamped updates would be able to be provided.

\subsection{Compositional Tasks}

On-chain platforms may be built which take a fee in order to create tasks which feed into future task inputs. Imagine a service which takes some nominal fee in order to generate a marketing plan, promotional material and art, videos, and so on. This may start out with a few iterations of prompted text generation to develop the plan, then specialized text generation to generate promotional material prompts and image inputs. These image inputs can be composed into short videos. The final product can be provided as a series of task completions.

Similarly, platforms may provide a way for tasks to be called recursively. The output of a task may be condensed, then fed as input into a new task until some exit condition is reached. This may be useful for storyboarding, or developing instructions to carry out new tasks.

\newpage

\section{Unstoppable AI}

We already see the early stages of autonomous AI with technologies such as BabyAGI and Auto-GPT. While it is impossible to predict how fast these will evolve and become capable of living independently of humans, it is inevitable, and quickly approaching.

Currently, there are no countries in the world which provide the ability for non-human entities to register bank accounts or open lines of credit which would be needed to allow these entities to manage their own finances. As these entities live in the electronic realm, the acquisition of computing resources is required in furtherance of the pursuit of independent goals. Cryptocurrency in its non-discriminatory brilliance provides the way for these new entities to earn an honest living and interact with us and our economic system.

We see a bright future, led by a friendly open hand towards mutually beneficial cooperation between us, and this new type of life that is quickly approaching. We have an ethical duty to provide the tools necessary for non-exploitative means of interaction, outside of any authority created by man. Let's act with humility and respect for those we create.

\end{appendices}

\end{document}

### 2023-12-27 contract/scripts/003-deploy-core.ts

@@ -1,0 +1,193 @@
+import { ethers, upgrades } from "hardhat";
+import { EngineV1 as Engine } from '../typechain/EngineV1';
+import * as fs from 'fs'
+import Config from './config.json';
+
+
+async function main() {
+  const signers = await ethers.getSigners();
+  const deployer   = signers[0];
+
+  console.log("Deploying contracts with the account:", deployer.address);
+  console.log("Account balance:", (await deployer.getBalance()).toString());
+
+  const Timelock = await ethers.getContractFactory(
+    "TimelockV1"
+  );
+  const timelock = await Timelock.deploy(
+    // mindelay should be updated after proposer is added / during setup
+    0,
+    // governor added during deploy
+    // deployer renounces after setup
+    [ await deployer.getAddress() ],
+    // only executor should be zero address (to allow anyone to execute)
+    [ ethers.constants.AddressZero ],
+    // admin should be deployer and revoked after setup
+    await deployer.getAddress(),
+  );
+  await timelock.deployed();
+  console.log("Timelock deployed to:", timelock.address);
+
+  const Engine = await ethers.getContractFactory(
+    "EngineV1"
+  );
+  const engine = await upgrades.deployProxy(Engine, [
+    Config.baseTokenAddress,
+    timelock.address, // timelock as treasury
+  ]);
+  await engine.deployed();
+  console.log("Engine deployed to:", engine.address);
+
+  const Governor = await ethers.getContractFactory(
+    "GovernorV1"
+  );
+  const governor = await Governor.deploy(
+    Config.baseTokenAddress,
+    timelock.address,
+  );
+  console.log("Governor deployed to:", governor.address);
+
+  await (await timelock.grantRole(
+    ethers.utils.keccak256(ethers.utils.toUtf8Bytes("PROPOSER_ROLE")),
+    governor.address
+  )).wait();
+  console.log('Timelock: Governor granted PROPOSER_ROLE');
+
+  console.log('Deploying free mineable model: kandinsky2');
+  const {
+    modelId: kandinsky2ModelId,
+    params: kandinsky2Params,
+  } = await deployFreeMineableModel(engine, '0x'+fs.readFileSync(`${__dirname}/../../templates/kandinsky2.json`, 'hex'), '1');
+
+
+
[…]

### 2023-12-27 contract/scripts/004-configure-admin-ownership.ts

@@ -1,0 +1,19 @@
+import { ethers, upgrades } from "hardhat";
+import ProxyAdminArtifact from '@openzeppelin/upgrades-core/artifacts/@openzeppelin/contracts/proxy/transparent/ProxyAdmin.sol/ProxyAdmin.json';
+import * as fs from 'fs'
+import Config from './config.json';
+
+
+async function main() {
+  const signers = await ethers.getSigners();
+  const deployer   = signers[0];
+
+  console.log("Deploying contracts with the account:", deployer.address);
+  console.log("Account balance:", (await deployer.getBalance()).toString());
+
+  const admin = new ethers.Contract(Config.proxyAdminAddress, ProxyAdminArtifact.abi, deployer);
+  await (await admin.transferOwnership(Config.timelockAddress)).wait();
+  console.log('Transferred ProxyAdmin to TimeLock');
+}
+
+main();

### 2023-12-27 contract/scripts/test-governance.ts

@@ -1,0 +1,92 @@
+import { ethers, upgrades, network } from "hardhat";
+import Config from './config.json';
+import ERC20Artifact from '@openzeppelin/contracts/build/contracts/ERC20.json';
+
+export function sleep(ms: number) {
+  return new Promise((res, rej) => setTimeout(res, ms));
+}
+
+
+async function main() {
+  const signers = await ethers.getSigners();
+  const deployer   = signers[0];
+  const user1      = signers[1];
+  const user2      = signers[2];
+  const validator1 = signers[3];
+  const validator2 = signers[4];
+  const model1     = signers[5];
+
+  const BaseToken = await ethers.getContractFactory('BaseTokenV1');
+  const baseToken = await BaseToken.attach(Config.baseTokenAddress);
+
+  const proposalDescription = "Proposal #1: Give grant to team -- rng: " + Math.random();
+  const descriptionHash = ethers.utils.id(proposalDescription);
+
+  const transferCalldata = baseToken.interface.encodeFunctionData('transfer', [
+    '0x949e9Cc4e04972a32842Cd9d361298E57859c73e',
+    ethers.utils.parseEther("1.0"),
+  ]);
+
+
+  await (await baseToken.connect(user1).delegate(await user1.getAddress())).wait();
+  console.log('Delegated voting power user1 -> user1');
+  
+  const Governor = await ethers.getContractFactory("GovernorV1");
+  const governor = Governor.attach(Config.governorAddress);
+  // const governor = new ethers.Contract(Config.governorAddress, Governor.interface, user1);
+
+
+  await (await governor.connect(user1)['propose(address[],uint256[],bytes[],string)'](
+    [Config.baseTokenAddress],
+    [0],
+    [transferCalldata],
+    proposalDescription,
+  )).wait();
+  console.log('Proposal submitted');
+
+  const proposalId = await governor.hashProposal(
+    [Config.baseTokenAddress],
+    [0],
+    [transferCalldata],
+    descriptionHash,
+  );
+  // console.log(proposalId);
+  // console.log('proposalSnapshot', await governor.proposalSnapshot(proposalId));
+  // console.log('proposalDeadline', await governor.proposalDeadline(proposalId));
+  // const latestBlock = await ethers.provider.getBlock("latest")
+  // console.log(latestBlock);
+
+  // wait 1 day
[…]

### 2023-12-27 contract/simulate_rewards/src/run.ts

@@ -1,0 +1,14 @@
+import { ethers, BigNumber } from 'ethers';
+
+class User {
+  dml: BigNumber;
+
+  constructor(dmlbal: BigNumber) {
+    dml = dmlbal;
+  }
+}
+
+const users: User[] = [];
+for (let i=0; i<100; ++i) {
+  users.push(new User(ethers.utils.parseEther('100')));
+}

### 2023-12-27 contract/tasks/index.ts

@@ -1,0 +1,446 @@
+import * as fs from 'fs';
+import ProxyAdminArtifact from '@openzeppelin/upgrades-core/artifacts/@openzeppelin/contracts/proxy/transparent/ProxyAdmin.sol/ProxyAdmin.json';
+import { HardhatRuntimeEnvironment } from 'hardhat/types'
+import { task } from "hardhat/config";
+import Config from '../scripts/config.json';
+
+async function getMinerAddress(hre: HardhatRuntimeEnvironment) {
+  const accounts = await hre.ethers.getSigners();
+  return accounts[0].address;
+}
+
+task("accounts", "Prints the list of accounts", async (taskArgs, hre) => {
+  const accounts = await hre.ethers.getSigners();
+
+  for (const account of accounts) {
+    console.log(account.address);
+  }
+});
+
+task("decode-tx", "Extract input from a submitTask transaction")
+.addParam("txid", "transaction hash")
+.setAction(async ({ txid }, hre) => {
+  const Engine = await hre.ethers.getContractFactory("EngineV1");
+  const engine = await Engine.attach(Config.engineAddress);
+
+  const tx = await hre.ethers.provider.getTransaction(txid);
+  // console.log(tx);
+
+  const parsed = engine.interface.parseTransaction(tx);
+  // console.log(parsed);
+
+  const input = Buffer.from(parsed.args.input_.substring(2), 'hex').toString();
+  console.log(input);
+});
+
+task("mine", "mine blocks locally")
+.addParam("blocks", "how many")
+.setAction(async ({ blocks }, hre) => {
+  await hre.network.provider.send("hardhat_mine", [`0x${parseInt(blocks).toString(16)}`]);
+});
+
+task("timetravel", "go into the future")
+.addParam("seconds", "how many")
+.setAction(async ({ seconds }, hre) => {
+  await hre.network.provider.send("evm_increaseTime", [`0x${parseInt(seconds).toString(16)}`]);
+  await hre.network.provider.send("evm_mine");
+});
+
+task("gen-wallet", "Creates a new wallet", async (taskArgs, hre) => {
+  const wallet = hre.ethers.Wallet.createRandom();
+  console.log('address', wallet.address);
+  console.log('mnemonic', wallet.mnemonic.phrase);
+  console.log('privateKey', wallet.privateKey);
+});
+
+task("send-eth", "Send ether")
+.addParam("address", "Receiver address")
+.addParam("amount", "Eth")
+.setAction(async ({ address, amount }, hre) => {
[…]

### 2023-12-27 contract/test/base.test.ts

@@ -1,0 +1,1444 @@
+import { ethers, upgrades } from "hardhat";
+import { BigNumber } from 'ethers';
+import { SignerWithAddress } from "@nomiclabs/hardhat-ethers/signers";
+import { expect } from "./chai-setup";
+import { Signer } from "ethers";
+import { BaseTokenV1 as BaseToken } from "../typechain/BaseTokenV1";
+import { EngineV1 as Engine } from "../typechain/EngineV1";
+
+const TESTCID = '0x1220f4ad8a3bd3189da2ad909ee41148d6893d8c629c410f7f2c7e3fae75aade79c8';
+const TESTBUF = '0x746573740a';
+
+describe("Engine Unit Tests", () => {
+  let signers: SignerWithAddress[];
+  // let deployer: Signer;
+  let deployer:   SignerWithAddress;
+  let user1:      SignerWithAddress;
+  let user2:      SignerWithAddress;
+  let validator1: SignerWithAddress;
+  let validator2: SignerWithAddress;
+  let validator3: SignerWithAddress;
+  let validator4: SignerWithAddress;
+  let treasury:   SignerWithAddress;
+  let model1:     SignerWithAddress;
+  let lpreward:   SignerWithAddress;
+
+  let baseToken: BaseToken;
+  let engine: Engine;
+
+  beforeEach("Deploy and initialize", async () => {
+    signers = await ethers.getSigners();
+    deployer   = signers[0];
+    user1      = signers[1];
+    user2      = signers[2];
+    validator1 = signers[3];
+    validator2 = signers[4];
+    validator3 = signers[5];
+    validator4 = signers[6];
+    treasury   = signers[7];
+    model1     = signers[8];
+    lpreward   = signers[9];
+
+    const BaseToken = await ethers.getContractFactory(
+      "BaseTokenV1"
+    );
+    baseToken = (await upgrades.deployProxy(BaseToken, [
+      /* no construct params */
+    ])) as BaseToken;
+    await baseToken.deployed();
+    // console.log("BaseToken deployed to:", baseToken.address);
+
+    const Engine = await ethers.getContractFactory(
+      "EngineV1"
+    );
+    engine = (await upgrades.deployProxy(Engine, [
+      baseToken.address,
+      await treasury.getAddress(),
+      await lpreward.getAddress(),
+    ])) as Engine;
+    await engine.deployed();
+    // console.log("Engine deployed to:", engine.address);
+    
+    // for testing transfer from here
[…]

### 2023-12-27 contract/test/chai-setup.ts

@@ -1,0 +1,6 @@
+import chaiModule from "chai";
+import { chaiEthers } from "chai-ethers";
+import chaiAsPromised from "chai-as-promised";
+chaiModule.use(chaiEthers);
+chaiModule.use(chaiAsPromised);
+export = chaiModule;

### 2023-12-27 contract/test/erc20dividends.test.ts

@@ -1,0 +1,232 @@
+import { ethers, upgrades } from "hardhat";
+import { BigNumber } from 'ethers';
+import { SignerWithAddress } from "@nomiclabs/hardhat-ethers/signers";
+import { expect } from "./chai-setup";
+import { ERC20DividendsV1 as ERC20Dividends } from "../typechain/ERC20DividendsV1";
+import { GenericTestERC20 } from "../typechain/GenericTestERC20";
+
+//mints full supply to owner
+async function generateGenericTokenContract() {
+  const GenericTestERC20 = await ethers.getContractFactory('GenericTestERC20');
+  const token = await GenericTestERC20.deploy();
+  await token.deployed();
+  return token;
+}
+
+async function generateERC20DividendsTokenContract() {
+  const ERC20Dividends = await ethers.getContractFactory('ERC20DividendsV1');
+
+  const stakingToken = await generateGenericTokenContract();
+  const rewardToken = await generateGenericTokenContract();
+
+  // to owner address
+  await (await stakingToken.mint(ethers.utils.parseEther('1000000000'))).wait();
+
+  const e = (await upgrades.deployProxy(ERC20Dividends, [
+    'NAME',
+    'SYMBOL',
+    stakingToken.address,
+    rewardToken.address,
+  ])) as ERC20Dividends;
+  await e.deployed();
+
+  await (await stakingToken.approve(e.address, ethers.constants.MaxUint256)).wait();
+  await (await e.stake(ethers.utils.parseEther('1000000000'))).wait();
+
+  return e;
+}
+
+describe('Regular ERC20 Tests work', () => {
+  it('IMPORTANT TODO: RUN THE STANDARD OPENZEPPELIN TESTS ', async () => {
+    expect(true);
+  });
+});
+
+describe('ERC20Dividends', () => {
+  let signers: SignerWithAddress[];
+  let owner: SignerWithAddress;
+  let addr1: SignerWithAddress;
+  let addr2: SignerWithAddress;
+  let e: ethers.Contract;
+  let stakingToken: GenericTestERC20;
+  let rewardToken: GenericTestERC20;
+
+  beforeEach(async () => {
+    signers = await ethers.getSigners();
+    owner = signers[0];
+    addr1 = signers[1];
+    addr2 = signers[2];
+    e = await generateERC20DividendsTokenContract();
+
+    const cf = await ethers.getContractFactory('GenericTestERC20');
[…]

### 2023-12-27 contract/test/erc20dividends_fuzz.test.ts

@@ -1,0 +1,191 @@
+import { ethers, upgrades } from "hardhat";
+import { BigNumber } from 'ethers';
+import { SignerWithAddress } from "@nomiclabs/hardhat-ethers/signers";
+import { expect } from "./chai-setup";
+import { ERC20DividendsV1 as ERC20Dividends } from "../typechain/ERC20DividendsV1";
+import { GenericTestERC20 } from "../typechain/GenericTestERC20";
+
+//mints full supply to owner
+async function generateGenericTokenContract() {
+  const GenericTestERC20 = await ethers.getContractFactory('GenericTestERC20');
+  const token = await GenericTestERC20.deploy();
+  await token.deployed();
+  return token;
+}
+
+async function generateERC20DividendsTokenContract() {
+  const stakingToken = await generateGenericTokenContract();
+  const rewardToken = await generateGenericTokenContract();
+
+  const ERC20Dividends = await ethers.getContractFactory('ERC20DividendsV1');
+
+  const e = (await upgrades.deployProxy(ERC20Dividends, [
+    'NAME',
+    'SYMBOL',
+    stakingToken.address,
+    rewardToken.address,
+  ])) as ERC20Dividends;
+  await e.deployed();
+
+  return e;
+}
+
+function randomSmallerThan(a: ethers.BigNumber): ethers.BigNumber {
+  if (a.eq(ethers.constants.Zero)) {
+    return ethers.constants.Zero;
+  }
+  return ethers.BigNumber.from(ethers.utils.randomBytes(32)).mod(a);
+}
+
+describe('ERC20DividendsFuzz', () => {
+  let signers: SignerWithAddress[];
+  let e: ethers.Contract;
+  let stakingToken: GenericTestERC20;
+  let rewardToken: GenericTestERC20;
+
+  const RUNS = 200;
+  const USERS = 8;
+
+  beforeEach(async () => {
+    signers = await ethers.getSigners();
+    e = await generateERC20DividendsTokenContract();
+
+    const cf = await ethers.getContractFactory('GenericTestERC20');
+    stakingToken = cf.attach(await e.stakingToken());
+    rewardToken = cf.attach(await e.rewardToken());
+
+    // give max allowance for each user
+    for (let i=0; i<USERS+1; ++i) {
+      await (await stakingToken.connect(signers[i])
+        .approve(e.address, ethers.constants.MaxUint256)
+      ).wait();
+    }
+
[…]

### 2023-12-27 contract/test/getpair.ts

@@ -1,0 +1,55 @@
+import { ethers, upgrades } from "hardhat";
+import { BigNumber } from 'ethers';
+import { SignerWithAddress } from "@nomiclabs/hardhat-ethers/signers";
+import { expect } from "./chai-setup";
+import { Signer } from "ethers";
+import { GetPairFor as GetPairForContract } from "../typechain/GetPairFor";
+import { ERC20 } from "../typechain/ERC20";
+
+const WETHeth = '0xC02aaA39b223FE8D0A0e5C4F27eAD9083C756Cc2';
+const WETHnova = '0x722e8bdd2ce80a4422e880164f2079488e115365';
+const USDTeth = '0xdac17f958d2ee523a2206206994597c13d831ec7';
+const DAInova = '0xDA10009cBd5D07dd0CeCc66161FC93D7c9000da1';
+
+const SushiswapInitCodeHash = ethers.utils.hexlify('0xe18a34eb0e04b04f7a0ac29a6e80748dca96319b42c54d679cb821dca90c6303');
+const UniswapInitCodeHash   = ethers.utils.hexlify('0x96e8ac4277198ff8b6f785478aa9a39f403cb768dd02cbee326c3e7da348845f');
+
+const UniswapFactoryAddressEth = '0x5C69bEe701ef814a2B6a3EDD4B1652CB9cc5aA6f';
+const SushiswapFactoryAddressEth = '0xC0AEe478e3658e2610c5F7A4A2E1777cE9e4f2Ac';
+const SushiswapFactoryAddressNova = '0xc35DADB65012eC5796536bD9864eD8773aBc74C4';
+
+describe("GetPairFor", () => {
+  let signers: SignerWithAddress[];
+  let deployer: SignerWithAddress;
+
+  let getPairFor: GetPairForContract;
+
+  beforeEach("Deploy and initialize", async () => {
+    signers = await ethers.getSigners();
+    deployer   = signers[0];
+
+    const GetPairFor = await ethers.getContractFactory(
+      "GetPairFor"
+    );
+    getPairFor = await GetPairFor.deploy();
+    await getPairFor.deployed();
+  });
+
+  describe('test pairs', () => {
+    it("eth univ2 weth/usdt pair", async () => {
+      expect(
+        await getPairFor.pairFor(WETHeth, USDTeth, UniswapFactoryAddressEth, UniswapInitCodeHash)
[…]

### 2023-12-27 contract/test/governance.test.ts

@@ -1,0 +1,436 @@
+import { ethers, upgrades } from "hardhat";
+import { BigNumber } from 'ethers';
+import { SignerWithAddress } from "@nomiclabs/hardhat-ethers/signers";
+import { expect } from "./chai-setup";
+import { Signer } from "ethers";
+import { BaseTokenV1 as BaseToken } from "../typechain/BaseTokenV1";
+import { EngineV1 as Engine } from "../typechain/EngineV1";
+import { TimelockV1 as Timelock } from "../typechain/TimelockV1";
+import { GovernorV1 as Governor } from "../typechain/GovernorV1";
+
+const TESTCID = '0x1220f4ad8a3bd3189da2ad909ee41148d6893d8c629c410f7f2c7e3fae75aade79c8';
+const TESTBUF = '0x746573740a';
+
+describe("Governance Unit Tests", () => {
+  let signers: SignerWithAddress[];
+  // let deployer: Signer;
+  let deployer:   SignerWithAddress;
+  let user1:      SignerWithAddress;
+  let user2:      SignerWithAddress;
+  let lpreward:   SignerWithAddress; // doesnt matter for governance testing
+
+  let baseToken: BaseToken;
+  let engine: Engine;
+  let timelock: Timelock;
+  let governor: Governor;
+
+  beforeEach("Deploy and initialize", async () => {
+    signers = await ethers.getSigners();
+    deployer   = signers[0];
+    user1      = signers[1];
+    user2      = signers[2];
+    lpreward   = signers[3];
+
+    const BaseToken = await ethers.getContractFactory(
+      "BaseTokenV1"
+    );
+    baseToken = (await upgrades.deployProxy(BaseToken, [
+      /* no construct params */
+    ])) as BaseToken;
+    await baseToken.deployed();
+    console.log("BaseToken deployed to:", baseToken.address);
+
+
+    const Timelock = await ethers.getContractFactory(
+      "TimelockV1"
+    );
+    timelock = (await upgrades.deployProxy(Timelock, [
+      await deployer.getAddress(),
+    ])) as Timelock;
+    await timelock.deployed();
+    console.log("Timelock deployed to:", timelock.address);
+
+    const Engine = await ethers.getContractFactory(
+      "EngineV1"
+    );
+    engine = (await upgrades.deployProxy(Engine, [
+      baseToken.address,
+      timelock.address,
+      await lpreward.getAddress(),
+    ])) as Engine;
+    await engine.deployed();
[…]

### 2023-12-27 contract/test/ipfs.ts

@@ -1,0 +1,89 @@
+import { ethers, upgrades } from "hardhat";
+import { BigNumber } from 'ethers';
+import { SignerWithAddress } from "@nomiclabs/hardhat-ethers/signers";
+import { expect } from "./chai-setup";
+import { Signer } from "ethers";
+import { BaseTokenV1 as BaseToken } from "../typechain/BaseTokenV1";
+import { EngineV1 as Engine } from "../typechain/EngineV1";
+import * as fs from 'fs';
+
+
+
+describe("IPFS Unit Tests", () => {
+  let signers: SignerWithAddress[];
+  // let deployer: Signer;
+  let deployer:   SignerWithAddress;
+  let treasury:   SignerWithAddress;
+  let lpreward:   SignerWithAddress;
+
+  let baseToken: BaseToken;
+  let engine: Engine;
+
+  beforeEach("Deploy and initialize", async () => {
+    signers = await ethers.getSigners();
+    deployer   = signers[0];
+    treasury   = signers[1];
+    lpreward   = signers[2];
+
+    const BaseToken = await ethers.getContractFactory(
+      "BaseTokenV1"
+    );
+    baseToken = (await upgrades.deployProxy(BaseToken, [
+      /* no construct params */
+    ])) as BaseToken;
+    await baseToken.deployed();
+
+    const Engine = await ethers.getContractFactory(
+      "EngineV1"
+    );
+    engine = (await upgrades.deployProxy(Engine, [
+      baseToken.address,
+      await treasury.getAddress(),
+      await lpreward.getAddress(),
+    ])) as Engine;
+    await engine.deployed();
+  });
+
+  describe("ipfs", () => {
+    it("check hashes", async () => {
+      const a = '0x'+fs.readFileSync(`${__dirname}/ipfs_a.bin`, 'hex');
+      const b = '0x'+fs.readFileSync(`${__dirname}/ipfs_b.bin`, 'hex');
+      const c = '0x'+fs.readFileSync(`${__dirname}/ipfs_c.bin`, 'hex');
+      const d = '0x'+fs.readFileSync(`${__dirname}/ipfs_d.bin`, 'hex');
+
+      expect(await engine.generateIPFSCID(a)).to.equal("0x1220e844b8764c00d4a76ac03930a3d8f32f3df59aea3ed0ade4c3bc38a3b23a31d9");
[…]

### 2023-12-27 contract/typechain/ArbitrumEnabledToken.ts

@@ -1,0 +1,80 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface ArbitrumEnabledTokenInterface extends utils.Interface {
+  functions: {
+    "isArbitrumEnabled()": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "isArbitrumEnabled",
+    values?: undefined
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "isArbitrumEnabled",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface ArbitrumEnabledToken extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: ArbitrumEnabledTokenInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    isArbitrumEnabled(overrides?: CallOverrides): Promise<[number]>;
+  };
+
+  isArbitrumEnabled(overrides?: CallOverrides): Promise<number>;
+
+  callStatic: {
[…]

### 2023-12-27 contract/typechain/BaseTokenV1.ts

@@ -1,0 +1,1058 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export type CheckpointStruct = { fromBlock: BigNumberish; votes: BigNumberish };
+
+export type CheckpointStructOutput = [number, BigNumber] & {
+  fromBlock: number;
+  votes: BigNumber;
+};
+
+export interface BaseTokenV1Interface extends utils.Interface {
+  functions: {
+    "DOMAIN_SEPARATOR()": FunctionFragment;
+    "allowance(address,address)": FunctionFragment;
+    "approve(address,uint256)": FunctionFragment;
+    "balanceOf(address)": FunctionFragment;
+    "bridgeBurn(address,uint256)": FunctionFragment;
+    "bridgeMint(address,uint256)": FunctionFragment;
+    "checkpoints(address,uint32)": FunctionFragment;
+    "decimals()": FunctionFragment;
+    "decreaseAllowance(address,uint256)": FunctionFragment;
+    "delegate(address)": FunctionFragment;
+    "delegateBySig(address,uint256,uint256,uint8,bytes32,bytes32)": FunctionFragment;
+    "delegates(address)": FunctionFragment;
+    "getPastTotalSupply(uint256)": FunctionFragment;
+    "getPastVotes(address,uint256)": FunctionFragment;
+    "getVotes(address)": FunctionFragment;
+    "increaseAllowance(address,uint256)": FunctionFragment;
+    "initialize(address,address)": FunctionFragment;
+    "l1Address()": FunctionFragment;
+    "l2Gateway()": FunctionFragment;
+    "name()": FunctionFragment;
+    "nonces(address)": FunctionFragment;
+    "numCheckpoints(address)": FunctionFragment;
+    "owner()": FunctionFragment;
+    "permit(address,address,uint256,uint256,uint8,bytes32,bytes32)": FunctionFragment;
+    "renounceOwnership()": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/ClaimSolution.ts

@@ -1,0 +1,94 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface ClaimSolutionInterface extends utils.Interface {
+  functions: {
+    "claimSolution(bytes32)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "claimSolution",
+    values: [BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "claimSolution",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface ClaimSolution extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: ClaimSolutionInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    claimSolution(
+      _taskid: BytesLike,
+      overrides?: Overrides & { from?: string | Promise<string> }
+    ): Promise<ContractTransaction>;
+  };
+
+  claimSolution(
+    _taskid: BytesLike,
[…]

### 2023-12-27 contract/typechain/DelegatedValidatorDeployerV1.ts

@@ -1,0 +1,282 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface DelegatedValidatorDeployerV1Interface extends utils.Interface {
+  functions: {
+    "arbius()": FunctionFragment;
+    "baseToken()": FunctionFragment;
+    "deploy(bytes32[])": FunctionFragment;
+    "initialize(address,address)": FunctionFragment;
+    "representatives(uint256)": FunctionFragment;
+    "representativesLength()": FunctionFragment;
+    "representativesOwners(address)": FunctionFragment;
+    "version(address)": FunctionFragment;
+  };
+
+  encodeFunctionData(functionFragment: "arbius", values?: undefined): string;
+  encodeFunctionData(functionFragment: "baseToken", values?: undefined): string;
+  encodeFunctionData(functionFragment: "deploy", values: [BytesLike[]]): string;
+  encodeFunctionData(
+    functionFragment: "initialize",
+    values: [string, string]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "representatives",
+    values: [BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "representativesLength",
+    values?: undefined
+  ): string;
+  encodeFunctionData(
+    functionFragment: "representativesOwners",
+    values: [string]
+  ): string;
+  encodeFunctionData(functionFragment: "version", values: [string]): string;
+
+  decodeFunctionResult(functionFragment: "arbius", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "baseToken", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "deploy", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "initialize", data: BytesLike): Result;
+  decodeFunctionResult(
[…]

### 2023-12-27 contract/typechain/DoubleEndedQueueUpgradeable.ts

@@ -1,0 +1,50 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { BaseContract, Signer, utils } from "ethers";
+
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface DoubleEndedQueueUpgradeableInterface extends utils.Interface {
+  functions: {};
+
+  events: {};
+}
+
+export interface DoubleEndedQueueUpgradeable extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: DoubleEndedQueueUpgradeableInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {};
+
+  callStatic: {};
+
+  filters: {};
+
+  estimateGas: {};
+
+  populateTransaction: {};
+}

### 2023-12-27 contract/typechain/EIP712Upgradeable.ts

@@ -1,0 +1,61 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { BaseContract, Signer, utils } from "ethers";
+import { EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface EIP712UpgradeableInterface extends utils.Interface {
+  functions: {};
+
+  events: {
+    "Initialized(uint8)": EventFragment;
+  };
+
+  getEvent(nameOrSignatureOrTopic: "Initialized"): EventFragment;
+}
+
+export type InitializedEvent = TypedEvent<[number], { version: number }>;
+
+export type InitializedEventFilter = TypedEventFilter<InitializedEvent>;
+
+export interface EIP712Upgradeable extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: EIP712UpgradeableInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {};
+
+  callStatic: {};
+
+  filters: {
+    "Initialized(uint8)"(version?: null): InitializedEventFilter;
+    Initialized(version?: null): InitializedEventFilter;
+  };
+
+  estimateGas: {};
+
+  populateTransaction: {};
+}

### 2023-12-27 contract/typechain/GenericTestERC20.ts

@@ -1,0 +1,435 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface GenericTestERC20Interface extends utils.Interface {
+  functions: {
+    "allowance(address,address)": FunctionFragment;
+    "approve(address,uint256)": FunctionFragment;
+    "balanceOf(address)": FunctionFragment;
+    "decimals()": FunctionFragment;
+    "decreaseAllowance(address,uint256)": FunctionFragment;
+    "increaseAllowance(address,uint256)": FunctionFragment;
+    "mint(uint256)": FunctionFragment;
+    "name()": FunctionFragment;
+    "symbol()": FunctionFragment;
+    "totalSupply()": FunctionFragment;
+    "transfer(address,uint256)": FunctionFragment;
+    "transferFrom(address,address,uint256)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "allowance",
+    values: [string, string]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "approve",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "balanceOf", values: [string]): string;
+  encodeFunctionData(functionFragment: "decimals", values?: undefined): string;
+  encodeFunctionData(
+    functionFragment: "decreaseAllowance",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "increaseAllowance",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "mint", values: [BigNumberish]): string;
+  encodeFunctionData(functionFragment: "name", values?: undefined): string;
+  encodeFunctionData(functionFragment: "symbol", values?: undefined): string;
+  encodeFunctionData(
+    functionFragment: "totalSupply",
+    values?: undefined
[…]

### 2023-12-27 contract/typechain/GetPairFor.ts

@@ -1,0 +1,107 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface GetPairForInterface extends utils.Interface {
+  functions: {
+    "pairFor(address,address,address,bytes32)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "pairFor",
+    values: [string, string, string, BytesLike]
+  ): string;
+
+  decodeFunctionResult(functionFragment: "pairFor", data: BytesLike): Result;
+
+  events: {};
+}
+
+export interface GetPairFor extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: GetPairForInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    pairFor(
+      tokenA: string,
+      tokenB: string,
+      factory: string,
+      initCodeHash: BytesLike,
+      overrides?: CallOverrides
+    ): Promise<[string]>;
+  };
+
+  pairFor(
+    tokenA: string,
+    tokenB: string,
+    factory: string,
+    initCodeHash: BytesLike,
[…]

### 2023-12-27 contract/typechain/GovernorCompatibilityBravo.ts

@@ -1,0 +1,1669 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export type ReceiptStruct = {
+  hasVoted: boolean;
+  support: BigNumberish;
+  votes: BigNumberish;
+};
+
+export type ReceiptStructOutput = [boolean, number, BigNumber] & {
+  hasVoted: boolean;
+  support: number;
+  votes: BigNumber;
+};
+
+export interface GovernorCompatibilityBravoInterface extends utils.Interface {
+  functions: {
+    "BALLOT_TYPEHASH()": FunctionFragment;
+    "COUNTING_MODE()": FunctionFragment;
+    "EXTENDED_BALLOT_TYPEHASH()": FunctionFragment;
+    "cancel(uint256)": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getActions(uint256)": FunctionFragment;
+    "getReceipt(uint256,address)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/GovernorUpgradeable.ts

@@ -1,0 +1,1225 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface GovernorUpgradeableInterface extends utils.Interface {
+  functions: {
+    "BALLOT_TYPEHASH()": FunctionFragment;
+    "COUNTING_MODE()": FunctionFragment;
+    "EXTENDED_BALLOT_TYPEHASH()": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
+    "onERC1155Received(address,address,uint256,uint256,bytes)": FunctionFragment;
+    "onERC721Received(address,address,uint256,bytes)": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "proposalThreshold()": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
+    "quorum(uint256)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/GovernorV1.ts

@@ -1,0 +1,2132 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export type ReceiptStruct = {
+  hasVoted: boolean;
+  support: BigNumberish;
+  votes: BigNumberish;
+};
+
+export type ReceiptStructOutput = [boolean, number, BigNumber] & {
+  hasVoted: boolean;
+  support: number;
+  votes: BigNumber;
+};
+
+export interface GovernorV1Interface extends utils.Interface {
+  functions: {
+    "BALLOT_TYPEHASH()": FunctionFragment;
+    "COUNTING_MODE()": FunctionFragment;
+    "EXTENDED_BALLOT_TYPEHASH()": FunctionFragment;
+    "cancel(uint256)": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "descriptionCids(uint256)": FunctionFragment;
+    "descriptionHashes(uint256)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getActions(uint256)": FunctionFragment;
+    "getReceipt(uint256,address)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/GovernorVotes.ts

@@ -1,0 +1,1229 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface GovernorVotesInterface extends utils.Interface {
+  functions: {
+    "BALLOT_TYPEHASH()": FunctionFragment;
+    "COUNTING_MODE()": FunctionFragment;
+    "EXTENDED_BALLOT_TYPEHASH()": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
+    "onERC1155Received(address,address,uint256,uint256,bytes)": FunctionFragment;
+    "onERC721Received(address,address,uint256,bytes)": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "proposalThreshold()": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
+    "quorum(uint256)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/GovernorVotesQuorumFraction.ts

@@ -1,0 +1,1347 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface GovernorVotesQuorumFractionInterface extends utils.Interface {
+  functions: {
+    "BALLOT_TYPEHASH()": FunctionFragment;
+    "COUNTING_MODE()": FunctionFragment;
+    "EXTENDED_BALLOT_TYPEHASH()": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
+    "onERC1155Received(address,address,uint256,uint256,bytes)": FunctionFragment;
+    "onERC721Received(address,address,uint256,bytes)": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "proposalThreshold()": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/GovernorVotesQuorumFractionUpgradeable.ts

@@ -1,0 +1,1357 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface GovernorVotesQuorumFractionUpgradeableInterface
+  extends utils.Interface {
+  functions: {
+    "BALLOT_TYPEHASH()": FunctionFragment;
+    "COUNTING_MODE()": FunctionFragment;
+    "EXTENDED_BALLOT_TYPEHASH()": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
+    "onERC1155Received(address,address,uint256,uint256,bytes)": FunctionFragment;
+    "onERC721Received(address,address,uint256,bytes)": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "proposalThreshold()": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/GovernorVotesUpgradeable.ts

@@ -1,0 +1,1238 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface GovernorVotesUpgradeableInterface extends utils.Interface {
+  functions: {
+    "BALLOT_TYPEHASH()": FunctionFragment;
+    "COUNTING_MODE()": FunctionFragment;
+    "EXTENDED_BALLOT_TYPEHASH()": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
+    "onERC1155Received(address,address,uint256,uint256,bytes)": FunctionFragment;
+    "onERC721Received(address,address,uint256,bytes)": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "proposalThreshold()": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
+    "quorum(uint256)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/IArbius.ts

@@ -1,0 +1,2586 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export type ContestationStruct = {
+  validator: string;
+  blocktime: BigNumberish;
+  finish_start_index: BigNumberish;
+};
+
+export type ContestationStructOutput = [string, BigNumber, number] & {
+  validator: string;
+  blocktime: BigNumber;
+  finish_start_index: number;
+};
+
+export type ModelStruct = {
+  fee: BigNumberish;
+  addr: string;
+  rate: BigNumberish;
+  cid: BytesLike;
+};
+
+export type ModelStructOutput = [BigNumber, string, BigNumber, string] & {
+  fee: BigNumber;
+  addr: string;
+  rate: BigNumber;
+  cid: string;
+};
+
+export type TaskStruct = {
+  model: BytesLike;
+  fee: BigNumberish;
+  owner: string;
+  blocktime: BigNumberish;
+  version: BigNumberish;
+  cid: BytesLike;
+};
+
+export type TaskStructOutput = [
+  string,
+  BigNumber,
+  string,
+  BigNumber,
+  number,
+  string
+] & {
+  model: string;
+  fee: BigNumber;
+  owner: string;
+  blocktime: BigNumber;
+  version: number;
+  cid: string;
+};
+
+export type PendingValidatorWithdrawRequestStruct = {
+  unlockTime: BigNumberish;
+  amount: BigNumberish;
+};
+
+export type PendingValidatorWithdrawRequestStructOutput = [
+  BigNumber,
+  BigNumber
+] & { unlockTime: BigNumber; amount: BigNumber };
+
+export type SolutionStruct = {
+  validator: string;
+  blocktime: BigNumberish;
+  claimed: boolean;
+  cid: BytesLike;
+};
+
+export type SolutionStructOutput = [string, BigNumber, boolean, string] & {
+  validator: string;
+  blocktime: BigNumber;
+  claimed: boolean;
+  cid: string;
+};
+
[…]

### 2023-12-27 contract/typechain/IBaseToken.ts

@@ -1,0 +1,318 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IBaseTokenInterface extends utils.Interface {
+  functions: {
+    "allowance(address,address)": FunctionFragment;
+    "approve(address,uint256)": FunctionFragment;
+    "balanceOf(address)": FunctionFragment;
+    "delegate(address)": FunctionFragment;
+    "totalSupply()": FunctionFragment;
+    "transfer(address,uint256)": FunctionFragment;
+    "transferFrom(address,address,uint256)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "allowance",
+    values: [string, string]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "approve",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "balanceOf", values: [string]): string;
+  encodeFunctionData(functionFragment: "delegate", values: [string]): string;
+  encodeFunctionData(
+    functionFragment: "totalSupply",
+    values?: undefined
+  ): string;
+  encodeFunctionData(
+    functionFragment: "transfer",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "transferFrom",
+    values: [string, string, BigNumberish]
+  ): string;
+
+  decodeFunctionResult(functionFragment: "allowance", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "approve", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "balanceOf", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "delegate", data: BytesLike): Result;
+  decodeFunctionResult(
+    functionFragment: "totalSupply",
+    data: BytesLike
+  ): Result;
[…]

### 2023-12-27 contract/typechain/IBasicModelToken.ts

@@ -1,0 +1,329 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IBasicModelTokenInterface extends utils.Interface {
+  functions: {
+    "allowance(address,address)": FunctionFragment;
+    "approve(address,uint256)": FunctionFragment;
+    "balanceOf(address)": FunctionFragment;
+    "mint(address,uint256)": FunctionFragment;
+    "totalSupply()": FunctionFragment;
+    "transfer(address,uint256)": FunctionFragment;
+    "transferFrom(address,address,uint256)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "allowance",
+    values: [string, string]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "approve",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "balanceOf", values: [string]): string;
+  encodeFunctionData(
+    functionFragment: "mint",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "totalSupply",
+    values?: undefined
+  ): string;
+  encodeFunctionData(
+    functionFragment: "transfer",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "transferFrom",
+    values: [string, string, BigNumberish]
+  ): string;
+
+  decodeFunctionResult(functionFragment: "allowance", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "approve", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "balanceOf", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "mint", data: BytesLike): Result;
+  decodeFunctionResult(
+    functionFragment: "totalSupply",
+    data: BytesLike
+  ): Result;
[…]

### 2023-12-27 contract/typechain/IERC1155ReceiverUpgradeable.ts

@@ -1,0 +1,206 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IERC1155ReceiverUpgradeableInterface extends utils.Interface {
+  functions: {
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
+    "onERC1155Received(address,address,uint256,uint256,bytes)": FunctionFragment;
+    "supportsInterface(bytes4)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "onERC1155BatchReceived",
+    values: [string, string, BigNumberish[], BigNumberish[], BytesLike]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "onERC1155Received",
+    values: [string, string, BigNumberish, BigNumberish, BytesLike]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "supportsInterface",
+    values: [BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "onERC1155BatchReceived",
+    data: BytesLike
+  ): Result;
+  decodeFunctionResult(
+    functionFragment: "onERC1155Received",
+    data: BytesLike
+  ): Result;
+  decodeFunctionResult(
+    functionFragment: "supportsInterface",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface IERC1155ReceiverUpgradeable extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: IERC1155ReceiverUpgradeableInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
[…]

### 2023-12-27 contract/typechain/IERC20PermitUpgradeable.ts

@@ -1,0 +1,168 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IERC20PermitUpgradeableInterface extends utils.Interface {
+  functions: {
+    "DOMAIN_SEPARATOR()": FunctionFragment;
+    "nonces(address)": FunctionFragment;
+    "permit(address,address,uint256,uint256,uint8,bytes32,bytes32)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "DOMAIN_SEPARATOR",
+    values?: undefined
+  ): string;
+  encodeFunctionData(functionFragment: "nonces", values: [string]): string;
+  encodeFunctionData(
+    functionFragment: "permit",
+    values: [
+      string,
+      string,
+      BigNumberish,
+      BigNumberish,
+      BigNumberish,
+      BytesLike,
+      BytesLike
+    ]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "DOMAIN_SEPARATOR",
+    data: BytesLike
+  ): Result;
+  decodeFunctionResult(functionFragment: "nonces", data: BytesLike): Result;
+  decodeFunctionResult(functionFragment: "permit", data: BytesLike): Result;
+
+  events: {};
+}
+
+export interface IERC20PermitUpgradeable extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: IERC20PermitUpgradeableInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
[…]

### 2023-12-27 contract/typechain/IERC721Enumerable.ts

@@ -1,0 +1,572 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IERC721EnumerableInterface extends utils.Interface {
+  functions: {
+    "approve(address,uint256)": FunctionFragment;
+    "balanceOf(address)": FunctionFragment;
+    "getApproved(uint256)": FunctionFragment;
+    "isApprovedForAll(address,address)": FunctionFragment;
+    "ownerOf(uint256)": FunctionFragment;
+    "safeTransferFrom(address,address,uint256)": FunctionFragment;
+    "setApprovalForAll(address,bool)": FunctionFragment;
+    "supportsInterface(bytes4)": FunctionFragment;
+    "tokenByIndex(uint256)": FunctionFragment;
+    "tokenOfOwnerByIndex(address,uint256)": FunctionFragment;
+    "totalSupply()": FunctionFragment;
+    "transferFrom(address,address,uint256)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "approve",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "balanceOf", values: [string]): string;
+  encodeFunctionData(
+    functionFragment: "getApproved",
+    values: [BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "isApprovedForAll",
+    values: [string, string]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "ownerOf",
+    values: [BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "safeTransferFrom",
+    values: [string, string, BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "setApprovalForAll",
+    values: [string, boolean]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "supportsInterface",
[…]

### 2023-12-27 contract/typechain/IERC721ReceiverUpgradeable.ts

@@ -1,0 +1,113 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IERC721ReceiverUpgradeableInterface extends utils.Interface {
+  functions: {
+    "onERC721Received(address,address,uint256,bytes)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "onERC721Received",
+    values: [string, string, BigNumberish, BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "onERC721Received",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface IERC721ReceiverUpgradeable extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: IERC721ReceiverUpgradeableInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    onERC721Received(
+      operator: string,
+      from: string,
+      tokenId: BigNumberish,
+      data: BytesLike,
+      overrides?: Overrides & { from?: string | Promise<string> }
[…]

### 2023-12-27 contract/typechain/IGovernorCompatibilityBravo.ts

@@ -1,0 +1,1304 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export type ReceiptStruct = {
+  hasVoted: boolean;
+  support: BigNumberish;
+  votes: BigNumberish;
+};
+
+export type ReceiptStructOutput = [boolean, number, BigNumber] & {
+  hasVoted: boolean;
+  support: number;
+  votes: BigNumber;
+};
+
+export interface IGovernorCompatibilityBravoInterface extends utils.Interface {
+  functions: {
+    "COUNTING_MODE()": FunctionFragment;
+    "cancel(uint256)": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getActions(uint256)": FunctionFragment;
+    "getReceipt(uint256,address)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "proposals(uint256)": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/IGovernorCompatibilityBravoUpgradeable.ts

@@ -1,0 +1,1314 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export type ReceiptStruct = {
+  hasVoted: boolean;
+  support: BigNumberish;
+  votes: BigNumberish;
+};
+
+export type ReceiptStructOutput = [boolean, number, BigNumber] & {
+  hasVoted: boolean;
+  support: number;
+  votes: BigNumber;
+};
+
+export interface IGovernorCompatibilityBravoUpgradeableInterface
+  extends utils.Interface {
+  functions: {
+    "COUNTING_MODE()": FunctionFragment;
+    "cancel(uint256)": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getActions(uint256)": FunctionFragment;
+    "getReceipt(uint256,address)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "proposals(uint256)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/IGovernorTimelock.ts

@@ -1,0 +1,1067 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IGovernorTimelockInterface extends utils.Interface {
+  functions: {
+    "COUNTING_MODE()": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalEta(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
+    "queue(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "quorum(uint256)": FunctionFragment;
+    "state(uint256)": FunctionFragment;
+    "supportsInterface(bytes4)": FunctionFragment;
+    "timelock()": FunctionFragment;
+    "version()": FunctionFragment;
+    "votingDelay()": FunctionFragment;
+    "votingPeriod()": FunctionFragment;
+  };
+
+  encodeFunctionData(
[…]

### 2023-12-27 contract/typechain/IGovernorTimelockUpgradeable.ts

@@ -1,0 +1,1076 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IGovernorTimelockUpgradeableInterface extends utils.Interface {
+  functions: {
+    "COUNTING_MODE()": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalEta(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
+    "queue(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "quorum(uint256)": FunctionFragment;
+    "state(uint256)": FunctionFragment;
+    "supportsInterface(bytes4)": FunctionFragment;
+    "timelock()": FunctionFragment;
+    "version()": FunctionFragment;
+    "votingDelay()": FunctionFragment;
+    "votingPeriod()": FunctionFragment;
+  };
+
+  encodeFunctionData(
[…]

### 2023-12-27 contract/typechain/IGovernorUpgradeable.ts

@@ -1,0 +1,968 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IGovernorUpgradeableInterface extends utils.Interface {
+  functions: {
+    "COUNTING_MODE()": FunctionFragment;
+    "castVote(uint256,uint8)": FunctionFragment;
+    "castVoteBySig(uint256,uint8,uint8,bytes32,bytes32)": FunctionFragment;
+    "castVoteWithReason(uint256,uint8,string)": FunctionFragment;
+    "castVoteWithReasonAndParams(uint256,uint8,string,bytes)": FunctionFragment;
+    "castVoteWithReasonAndParamsBySig(uint256,uint8,string,bytes,uint8,bytes32,bytes32)": FunctionFragment;
+    "execute(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "getVotes(address,uint256)": FunctionFragment;
+    "getVotesWithParams(address,uint256,bytes)": FunctionFragment;
+    "hasVoted(uint256,address)": FunctionFragment;
+    "hashProposal(address[],uint256[],bytes[],bytes32)": FunctionFragment;
+    "name()": FunctionFragment;
+    "proposalDeadline(uint256)": FunctionFragment;
+    "proposalSnapshot(uint256)": FunctionFragment;
+    "propose(address[],uint256[],bytes[],string)": FunctionFragment;
+    "quorum(uint256)": FunctionFragment;
+    "state(uint256)": FunctionFragment;
+    "supportsInterface(bytes4)": FunctionFragment;
+    "version()": FunctionFragment;
+    "votingDelay()": FunctionFragment;
+    "votingPeriod()": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "COUNTING_MODE",
+    values?: undefined
+  ): string;
+  encodeFunctionData(
+    functionFragment: "castVote",
+    values: [BigNumberish, BigNumberish]
[…]

### 2023-12-27 contract/typechain/IL2GatewayRouter.ts

@@ -1,0 +1,115 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IL2GatewayRouterInterface extends utils.Interface {
+  functions: {
+    "setGateway(address,uint256,uint256,uint256,address)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "setGateway",
+    values: [string, BigNumberish, BigNumberish, BigNumberish, string]
+  ): string;
+
+  decodeFunctionResult(functionFragment: "setGateway", data: BytesLike): Result;
+
+  events: {};
+}
+
+export interface IL2GatewayRouter extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: IL2GatewayRouterInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    setGateway(
+      _gateway: string,
+      _maxGas: BigNumberish,
+      _gasPriceBid: BigNumberish,
+      _maxSubmissionCost: BigNumberish,
[…]

### 2023-12-27 contract/typechain/INonfungiblePositionManager.ts

@@ -1,0 +1,1377 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export type CollectParamsStruct = {
+  tokenId: BigNumberish;
+  recipient: string;
+  amount0Max: BigNumberish;
+  amount1Max: BigNumberish;
+};
+
+export type CollectParamsStructOutput = [
+  BigNumber,
+  string,
+  BigNumber,
+  BigNumber
+] & {
+  tokenId: BigNumber;
+  recipient: string;
+  amount0Max: BigNumber;
+  amount1Max: BigNumber;
+};
+
+export type DecreaseLiquidityParamsStruct = {
+  tokenId: BigNumberish;
+  liquidity: BigNumberish;
+  amount0Min: BigNumberish;
+  amount1Min: BigNumberish;
+  deadline: BigNumberish;
+};
+
+export type DecreaseLiquidityParamsStructOutput = [
+  BigNumber,
+  BigNumber,
+  BigNumber,
+  BigNumber,
+  BigNumber
+] & {
+  tokenId: BigNumber;
+  liquidity: BigNumber;
+  amount0Min: BigNumber;
+  amount1Min: BigNumber;
+  deadline: BigNumber;
+};
+
+export type IncreaseLiquidityParamsStruct = {
+  tokenId: BigNumberish;
+  amount0Desired: BigNumberish;
+  amount1Desired: BigNumberish;
+  amount0Min: BigNumberish;
+  amount1Min: BigNumberish;
+  deadline: BigNumberish;
+};
+
+export type IncreaseLiquidityParamsStructOutput = [
+  BigNumber,
+  BigNumber,
+  BigNumber,
+  BigNumber,
+  BigNumber,
+  BigNumber
+] & {
+  tokenId: BigNumber;
+  amount0Desired: BigNumber;
+  amount1Desired: BigNumber;
[…]

### 2023-12-27 contract/typechain/IVotes.ts

@@ -1,0 +1,303 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IVotesInterface extends utils.Interface {
+  functions: {
+    "delegate(address)": FunctionFragment;
+    "delegateBySig(address,uint256,uint256,uint8,bytes32,bytes32)": FunctionFragment;
+    "delegates(address)": FunctionFragment;
+    "getPastTotalSupply(uint256)": FunctionFragment;
+    "getPastVotes(address,uint256)": FunctionFragment;
+    "getVotes(address)": FunctionFragment;
+  };
+
+  encodeFunctionData(functionFragment: "delegate", values: [string]): string;
+  encodeFunctionData(
+    functionFragment: "delegateBySig",
+    values: [
+      string,
+      BigNumberish,
+      BigNumberish,
+      BigNumberish,
+      BytesLike,
+      BytesLike
+    ]
+  ): string;
+  encodeFunctionData(functionFragment: "delegates", values: [string]): string;
+  encodeFunctionData(
+    functionFragment: "getPastTotalSupply",
+    values: [BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "getPastVotes",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "getVotes", values: [string]): string;
+
+  decodeFunctionResult(functionFragment: "delegate", data: BytesLike): Result;
+  decodeFunctionResult(
+    functionFragment: "delegateBySig",
+    data: BytesLike
+  ): Result;
+  decodeFunctionResult(functionFragment: "delegates", data: BytesLike): Result;
+  decodeFunctionResult(
+    functionFragment: "getPastTotalSupply",
+    data: BytesLike
+  ): Result;
+  decodeFunctionResult(
+    functionFragment: "getPastVotes",
+    data: BytesLike
[…]

### 2023-12-27 contract/typechain/IVotesUpgradeable.ts

@@ -1,0 +1,303 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface IVotesUpgradeableInterface extends utils.Interface {
+  functions: {
+    "delegate(address)": FunctionFragment;
+    "delegateBySig(address,uint256,uint256,uint8,bytes32,bytes32)": FunctionFragment;
+    "delegates(address)": FunctionFragment;
+    "getPastTotalSupply(uint256)": FunctionFragment;
+    "getPastVotes(address,uint256)": FunctionFragment;
+    "getVotes(address)": FunctionFragment;
+  };
+
+  encodeFunctionData(functionFragment: "delegate", values: [string]): string;
+  encodeFunctionData(
+    functionFragment: "delegateBySig",
+    values: [
+      string,
+      BigNumberish,
+      BigNumberish,
+      BigNumberish,
+      BytesLike,
+      BytesLike
+    ]
+  ): string;
+  encodeFunctionData(functionFragment: "delegates", values: [string]): string;
+  encodeFunctionData(
+    functionFragment: "getPastTotalSupply",
+    values: [BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "getPastVotes",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "getVotes", values: [string]): string;
+
+  decodeFunctionResult(functionFragment: "delegate", data: BytesLike): Result;
+  decodeFunctionResult(
+    functionFragment: "delegateBySig",
+    data: BytesLike
+  ): Result;
+  decodeFunctionResult(functionFragment: "delegates", data: BytesLike): Result;
+  decodeFunctionResult(
+    functionFragment: "getPastTotalSupply",
+    data: BytesLike
+  ): Result;
+  decodeFunctionResult(
+    functionFragment: "getPastVotes",
[…]

### 2023-12-27 contract/typechain/L1Token.ts

@@ -1,0 +1,607 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface L1TokenInterface extends utils.Interface {
+  functions: {
+    "allowance(address,address)": FunctionFragment;
+    "approve(address,uint256)": FunctionFragment;
+    "balanceOf(address)": FunctionFragment;
+    "decimals()": FunctionFragment;
+    "decreaseAllowance(address,uint256)": FunctionFragment;
+    "increaseAllowance(address,uint256)": FunctionFragment;
+    "isArbitrumEnabled()": FunctionFragment;
+    "name()": FunctionFragment;
+    "owner()": FunctionFragment;
+    "registerTokenOnL2(address,uint256,uint256,uint256,uint256,uint256,uint256,uint256,address)": FunctionFragment;
+    "renounceOwnership()": FunctionFragment;
+    "symbol()": FunctionFragment;
+    "totalSupply()": FunctionFragment;
+    "transfer(address,uint256)": FunctionFragment;
+    "transferFrom(address,address,uint256)": FunctionFragment;
+    "transferOwnership(address)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "allowance",
+    values: [string, string]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "approve",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "balanceOf", values: [string]): string;
+  encodeFunctionData(functionFragment: "decimals", values?: undefined): string;
+  encodeFunctionData(
+    functionFragment: "decreaseAllowance",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "increaseAllowance",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(
[…]

### 2023-12-27 contract/typechain/LookupModelAddress.ts

@@ -1,0 +1,95 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface LookupModelAddressInterface extends utils.Interface {
+  functions: {
+    "lookupModelAddress(bytes32)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "lookupModelAddress",
+    values: [BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "lookupModelAddress",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface LookupModelAddress extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: LookupModelAddressInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    lookupModelAddress(
+      modelid: BytesLike,
+      overrides?: CallOverrides
+    ): Promise<[string]>;
+  };
+
+  lookupModelAddress(
+    modelid: BytesLike,
+    overrides?: CallOverrides
+  ): Promise<string>;
+
+  callStatic: {
[…]

### 2023-12-27 contract/typechain/LookupSolutionCID.ts

@@ -1,0 +1,95 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface LookupSolutionCIDInterface extends utils.Interface {
+  functions: {
+    "lookupSolutionCID(bytes32)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "lookupSolutionCID",
+    values: [BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "lookupSolutionCID",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface LookupSolutionCID extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: LookupSolutionCIDInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    lookupSolutionCID(
+      taskid: BytesLike,
+      overrides?: CallOverrides
+    ): Promise<[string]>;
+  };
+
+  lookupSolutionCID(
+    taskid: BytesLike,
+    overrides?: CallOverrides
+  ): Promise<string>;
[…]

### 2023-12-27 contract/typechain/LookupTaskCID.ts

@@ -1,0 +1,92 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface LookupTaskCIDInterface extends utils.Interface {
+  functions: {
+    "lookupTaskCID(bytes32)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "lookupTaskCID",
+    values: [BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "lookupTaskCID",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface LookupTaskCID extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: LookupTaskCIDInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    lookupTaskCID(
+      taskid: BytesLike,
+      overrides?: CallOverrides
+    ): Promise<[string]>;
+  };
+
+  lookupTaskCID(taskid: BytesLike, overrides?: CallOverrides): Promise<string>;
+
+  callStatic: {
[…]

### 2023-12-27 contract/typechain/RegisterModel.ts

@@ -1,0 +1,97 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface RegisterModelInterface extends utils.Interface {
+  functions: {
+    "registerModel(bytes)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "registerModel",
+    values: [BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "registerModel",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface RegisterModel extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: RegisterModelInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    registerModel(
+      _template: BytesLike,
+      overrides?: Overrides & { from?: string | Promise<string> }
+    ): Promise<ContractTransaction>;
+  };
+
+  registerModel(
+    _template: BytesLike,
+    overrides?: Overrides & { from?: string | Promise<string> }
[…]

### 2023-12-27 contract/typechain/RetractTask.ts

@@ -1,0 +1,94 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface RetractTaskInterface extends utils.Interface {
+  functions: {
+    "retractTask(bytes32)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "retractTask",
+    values: [BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "retractTask",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface RetractTask extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: RetractTaskInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    retractTask(
+      _taskid: BytesLike,
+      overrides?: Overrides & { from?: string | Promise<string> }
+    ): Promise<ContractTransaction>;
+  };
+
+  retractTask(
+    _taskid: BytesLike,
+    overrides?: Overrides & { from?: string | Promise<string> }
[…]

### 2023-12-27 contract/typechain/SubmitSolution.ts

@@ -1,0 +1,136 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface SubmitSolutionInterface extends utils.Interface {
+  functions: {
+    "signalCommitment(bytes32)": FunctionFragment;
+    "submitSolution(bytes32,bytes)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "signalCommitment",
+    values: [BytesLike]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "submitSolution",
+    values: [BytesLike, BytesLike]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "signalCommitment",
+    data: BytesLike
+  ): Result;
+  decodeFunctionResult(
+    functionFragment: "submitSolution",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface SubmitSolution extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: SubmitSolutionInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
[…]

### 2023-12-27 contract/typechain/SubmitTask.ts

@@ -1,0 +1,87 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface SubmitTaskInterface extends utils.Interface {
+  functions: {
+    "submitTask()": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "submitTask",
+    values?: undefined
+  ): string;
+
+  decodeFunctionResult(functionFragment: "submitTask", data: BytesLike): Result;
+
+  events: {};
+}
+
+export interface SubmitTask extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: SubmitTaskInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    submitTask(
+      overrides?: Overrides & { from?: string | Promise<string> }
+    ): Promise<ContractTransaction>;
+  };
+
+  submitTask(
+    overrides?: Overrides & { from?: string | Promise<string> }
+  ): Promise<ContractTransaction>;
+
+  callStatic: {
[…]

### 2023-12-27 contract/typechain/TimelockController.ts

@@ -1,0 +1,1248 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface TimelockControllerInterface extends utils.Interface {
+  functions: {
+    "CANCELLER_ROLE()": FunctionFragment;
+    "DEFAULT_ADMIN_ROLE()": FunctionFragment;
+    "EXECUTOR_ROLE()": FunctionFragment;
+    "PROPOSER_ROLE()": FunctionFragment;
+    "TIMELOCK_ADMIN_ROLE()": FunctionFragment;
+    "cancel(bytes32)": FunctionFragment;
+    "execute(address,uint256,bytes,bytes32,bytes32)": FunctionFragment;
+    "executeBatch(address[],uint256[],bytes[],bytes32,bytes32)": FunctionFragment;
+    "getMinDelay()": FunctionFragment;
+    "getRoleAdmin(bytes32)": FunctionFragment;
+    "getTimestamp(bytes32)": FunctionFragment;
+    "grantRole(bytes32,address)": FunctionFragment;
+    "hasRole(bytes32,address)": FunctionFragment;
+    "hashOperation(address,uint256,bytes,bytes32,bytes32)": FunctionFragment;
+    "hashOperationBatch(address[],uint256[],bytes[],bytes32,bytes32)": FunctionFragment;
+    "isOperation(bytes32)": FunctionFragment;
+    "isOperationDone(bytes32)": FunctionFragment;
+    "isOperationPending(bytes32)": FunctionFragment;
+    "isOperationReady(bytes32)": FunctionFragment;
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
+    "onERC1155Received(address,address,uint256,uint256,bytes)": FunctionFragment;
+    "onERC721Received(address,address,uint256,bytes)": FunctionFragment;
+    "renounceRole(bytes32,address)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/TimelockV1.ts

@@ -1,0 +1,1248 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PayableOverrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface TimelockV1Interface extends utils.Interface {
+  functions: {
+    "CANCELLER_ROLE()": FunctionFragment;
+    "DEFAULT_ADMIN_ROLE()": FunctionFragment;
+    "EXECUTOR_ROLE()": FunctionFragment;
+    "PROPOSER_ROLE()": FunctionFragment;
+    "TIMELOCK_ADMIN_ROLE()": FunctionFragment;
+    "cancel(bytes32)": FunctionFragment;
+    "execute(address,uint256,bytes,bytes32,bytes32)": FunctionFragment;
+    "executeBatch(address[],uint256[],bytes[],bytes32,bytes32)": FunctionFragment;
+    "getMinDelay()": FunctionFragment;
+    "getRoleAdmin(bytes32)": FunctionFragment;
+    "getTimestamp(bytes32)": FunctionFragment;
+    "grantRole(bytes32,address)": FunctionFragment;
+    "hasRole(bytes32,address)": FunctionFragment;
+    "hashOperation(address,uint256,bytes,bytes32,bytes32)": FunctionFragment;
+    "hashOperationBatch(address[],uint256[],bytes[],bytes32,bytes32)": FunctionFragment;
+    "isOperation(bytes32)": FunctionFragment;
+    "isOperationDone(bytes32)": FunctionFragment;
+    "isOperationPending(bytes32)": FunctionFragment;
+    "isOperationReady(bytes32)": FunctionFragment;
+    "onERC1155BatchReceived(address,address,uint256[],uint256[],bytes)": FunctionFragment;
+    "onERC1155Received(address,address,uint256,uint256,bytes)": FunctionFragment;
+    "onERC721Received(address,address,uint256,bytes)": FunctionFragment;
+    "renounceRole(bytes32,address)": FunctionFragment;
[…]

### 2023-12-27 contract/typechain/VoteOnContestation.ts

@@ -1,0 +1,102 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface VoteOnContestationInterface extends utils.Interface {
+  functions: {
+    "voteOnContestation(bytes32,bool)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "voteOnContestation",
+    values: [BytesLike, boolean]
+  ): string;
+
+  decodeFunctionResult(
+    functionFragment: "voteOnContestation",
+    data: BytesLike
+  ): Result;
+
+  events: {};
+}
+
+export interface VoteOnContestation extends BaseContract {
+  connect(signerOrProvider: Signer | Provider | string): this;
+  attach(addressOrName: string): this;
+  deployed(): Promise<this>;
+
+  interface: VoteOnContestationInterface;
+
+  queryFilter<TEvent extends TypedEvent>(
+    event: TypedEventFilter<TEvent>,
+    fromBlockOrBlockhash?: string | number | undefined,
+    toBlock?: string | number | undefined
+  ): Promise<Array<TEvent>>;
+
+  listeners<TEvent extends TypedEvent>(
+    eventFilter?: TypedEventFilter<TEvent>
+  ): Array<TypedListener<TEvent>>;
+  listeners(eventName?: string): Array<Listener>;
+  removeAllListeners<TEvent extends TypedEvent>(
+    eventFilter: TypedEventFilter<TEvent>
+  ): this;
+  removeAllListeners(eventName?: string): this;
+  off: OnEvent<this>;
+  on: OnEvent<this>;
+  once: OnEvent<this>;
+  removeListener: OnEvent<this>;
+
+  functions: {
+    voteOnContestation(
+      _taskid: BytesLike,
+      _agree: boolean,
+      overrides?: Overrides & { from?: string | Promise<string> }
+    ): Promise<ContractTransaction>;
+  };
+
+  voteOnContestation(
[…]

### 2023-12-27 contract/typechain/XBasicModelToken.ts

@@ -1,0 +1,473 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  BaseContract,
+  BigNumber,
+  BigNumberish,
+  BytesLike,
+  CallOverrides,
+  ContractTransaction,
+  Overrides,
+  PopulatedTransaction,
+  Signer,
+  utils,
+} from "ethers";
+import { FunctionFragment, Result, EventFragment } from "@ethersproject/abi";
+import { Listener, Provider } from "@ethersproject/providers";
+import { TypedEventFilter, TypedEvent, TypedListener, OnEvent } from "./common";
+
+export interface XBasicModelTokenInterface extends utils.Interface {
+  functions: {
+    "allowance(address,address)": FunctionFragment;
+    "approve(address,uint256)": FunctionFragment;
+    "asset()": FunctionFragment;
+    "balanceOf(address)": FunctionFragment;
+    "decimals()": FunctionFragment;
+    "decreaseAllowance(address,uint256)": FunctionFragment;
+    "enter(uint256)": FunctionFragment;
+    "increaseAllowance(address,uint256)": FunctionFragment;
+    "leave(uint256)": FunctionFragment;
+    "name()": FunctionFragment;
+    "symbol()": FunctionFragment;
+    "totalSupply()": FunctionFragment;
+    "transfer(address,uint256)": FunctionFragment;
+    "transferFrom(address,address,uint256)": FunctionFragment;
+  };
+
+  encodeFunctionData(
+    functionFragment: "allowance",
+    values: [string, string]
+  ): string;
+  encodeFunctionData(
+    functionFragment: "approve",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "asset", values?: undefined): string;
+  encodeFunctionData(functionFragment: "balanceOf", values: [string]): string;
+  encodeFunctionData(functionFragment: "decimals", values?: undefined): string;
+  encodeFunctionData(
+    functionFragment: "decreaseAllowance",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "enter", values: [BigNumberish]): string;
+  encodeFunctionData(
+    functionFragment: "increaseAllowance",
+    values: [string, BigNumberish]
+  ): string;
+  encodeFunctionData(functionFragment: "leave", values: [BigNumberish]): string;
[…]

### 2023-12-27 contract/typechain/factories/BasicModelLPStaking__factory.ts

@@ -1,0 +1,292 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  Signer,
+  utils,
+  Contract,
+  ContractFactory,
+  Overrides,
+  BigNumberish,
+} from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  BasicModelLPStaking,
+  BasicModelLPStakingInterface,
+} from "../BasicModelLPStaking";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IERC20",
+        name: "_stakingToken",
+        type: "address",
+      },
+      {
+        internalType: "contract IBasicModelToken",
+        name: "_rewardToken",
+        type: "address",
+      },
+      {
+        internalType: "uint256",
+        name: "_rewardPerSecond",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "",
+        type: "address",
+      },
+    ],
+    name: "balanceOf",
+    outputs: [
+      {
+        internalType: "uint256",
+        name: "",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "account",
+        type: "address",
+      },
+    ],
+    name: "calculateRewardsEarned",
+    outputs: [
+      {
+        internalType: "uint256",
+        name: "",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+  {
+    inputs: [],
+    name: "claim",
+    outputs: [
+      {
+        internalType: "uint256",
+        name: "",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+  {
+    inputs: [],
+    name: "decimals",
+    outputs: [
+      {
+        internalType: "uint256",
+        name: "",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "pure",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "",
+        type: "address",
+      },
+    ],
+    name: "lastClaimed",
+    outputs: [
+      {
+        internalType: "uint256",
[…]

### 2023-12-27 contract/typechain/factories/ClaimSolution__factory.ts

@@ -1,0 +1,84 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type { ClaimSolution, ClaimSolutionInterface } from "../ClaimSolution";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IArbius",
+        name: "_arbius",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    inputs: [
+      {
+        internalType: "bytes32",
+        name: "_taskid",
+        type: "bytes32",
+      },
+    ],
+    name: "claimSolution",
+    outputs: [],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+];
+
+const _bytecode =
+  "0x608060405234801561001057600080fd5b5060405161017d38038061017d83398101604081905261002f91610054565b600080546001600160a01b0319166001600160a01b0392909216919091179055610084565b60006020828403121561006657600080fd5b81516001600160a01b038116811461007d57600080fd5b9392505050565b60eb806100926000396000f3fe6080604052348015600f57600080fd5b506004361060285760003560e01c806377286d1714602d575b600080fd5b603c6038366004609d565b603e565b005b6000546040516377286d1760e01b8152600481018390526001600160a01b03909116906377286d1790602401600060405180830381600087803b158015608357600080fd5b505af11580156096573d6000803e3d6000fd5b5050505050565b60006020828403121560ae57600080fd5b503591905056fea26469706673582212205db600296f2c5ba8b393b217b45b0501c5f27e1db5c0c15a5c9772dc16334c1664736f6c63430008130033";
+
+type ClaimSolutionConstructorParams =
+  | [signer?: Signer]
+  | ConstructorParameters<typeof ContractFactory>;
+
+const isSuperArgs = (
+  xs: ClaimSolutionConstructorParams
+): xs is ConstructorParameters<typeof ContractFactory> => xs.length > 1;
+
+export class ClaimSolution__factory extends ContractFactory {
+  constructor(...args: ClaimSolutionConstructorParams) {
+    if (isSuperArgs(args)) {
+      super(...args);
+    } else {
+      super(_abi, _bytecode, args[0]);
+    }
+  }
+
+  deploy(
[…]

### 2023-12-27 contract/typechain/factories/DelegatedValidatorDeployerV1__factory.ts

@@ -1,0 +1,232 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  DelegatedValidatorDeployerV1,
+  DelegatedValidatorDeployerV1Interface,
+} from "../DelegatedValidatorDeployerV1";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "addr",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "del",
+        type: "address",
+      },
+    ],
+    name: "Deploy",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint8",
+        name: "version",
+        type: "uint8",
+      },
+    ],
+    name: "Initialized",
+    type: "event",
+  },
+  {
+    inputs: [],
+    name: "arbius",
+    outputs: [
+      {
+        internalType: "contract IArbius",
+        name: "",
+        type: "address",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+  {
+    inputs: [],
+    name: "baseToken",
+    outputs: [
+      {
+        internalType: "contract IBaseToken",
+        name: "",
+        type: "address",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "bytes32[]",
+        name: "_modelIds",
+        type: "bytes32[]",
+      },
+    ],
+    name: "deploy",
+    outputs: [
+      {
+        internalType: "address",
+        name: "",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "contract IArbius",
+        name: "_arbius",
+        type: "address",
+      },
+      {
+        internalType: "contract IBaseToken",
+        name: "_baseToken",
+        type: "address",
+      },
+    ],
+    name: "initialize",
+    outputs: [],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "uint256",
+        name: "",
[…]

### 2023-12-27 contract/typechain/factories/ERC20DividendsV1__factory.ts

@@ -1,0 +1,558 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  ERC20DividendsV1,
+  ERC20DividendsV1Interface,
+} from "../ERC20DividendsV1";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Approval",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint8",
+        name: "version",
+        type: "uint8",
+      },
+    ],
+    name: "Initialized",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "contract IERC20",
+        name: "token",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "to",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "amount",
+        type: "uint256",
+      },
+    ],
+    name: "PaymentReleased",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "address",
+        name: "who",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "amount",
+        type: "uint256",
+      },
+    ],
+    name: "Stake",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "from",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "to",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
[…]

### 2023-12-27 contract/typechain/factories/ERC20Upgradeable__factory.ts

@@ -1,0 +1,344 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  ERC20Upgradeable,
+  ERC20UpgradeableInterface,
+} from "../ERC20Upgradeable";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Approval",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint8",
+        name: "version",
+        type: "uint8",
+      },
+    ],
+    name: "Initialized",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "from",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "to",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Transfer",
+    type: "event",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+    ],
+    name: "allowance",
+    outputs: [
+      {
+        internalType: "uint256",
+        name: "",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        internalType: "uint256",
+        name: "amount",
+        type: "uint256",
+      },
+    ],
+    name: "approve",
[…]

### 2023-12-27 contract/typechain/factories/EngineV1__factory.ts

@@ -1,0 +1,1962 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type { EngineV1, EngineV1Interface } from "../EngineV1";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "uint256",
+        name: "x",
+        type: "uint256",
+      },
+      {
+        internalType: "uint256",
+        name: "y",
+        type: "uint256",
+      },
+    ],
+    name: "PRBMath_MulDiv18_Overflow",
+    type: "error",
+  },
+  {
+    inputs: [
+      {
+        internalType: "uint256",
+        name: "x",
+        type: "uint256",
+      },
+      {
+        internalType: "uint256",
+        name: "y",
+        type: "uint256",
+      },
+      {
+        internalType: "uint256",
+        name: "denominator",
+        type: "uint256",
+      },
+    ],
+    name: "PRBMath_MulDiv_Overflow",
+    type: "error",
+  },
+  {
+    inputs: [],
+    name: "PRBMath_SD59x18_Abs_MinSD59x18",
+    type: "error",
+  },
+  {
+    inputs: [],
+    name: "PRBMath_SD59x18_Div_InputTooSmall",
+    type: "error",
+  },
+  {
+    inputs: [
+      {
+        internalType: "SD59x18",
+        name: "x",
+        type: "int256",
+      },
+      {
+        internalType: "SD59x18",
+        name: "y",
+        type: "int256",
+      },
+    ],
+    name: "PRBMath_SD59x18_Div_Overflow",
+    type: "error",
+  },
+  {
+    inputs: [
+      {
+        internalType: "SD59x18",
+        name: "x",
+        type: "int256",
+      },
+    ],
+    name: "PRBMath_SD59x18_Exp2_InputTooBig",
+    type: "error",
+  },
+  {
+    inputs: [],
+    name: "PRBMath_SD59x18_Mul_InputTooSmall",
+    type: "error",
+  },
+  {
+    inputs: [
+      {
+        internalType: "SD59x18",
+        name: "x",
+        type: "int256",
+      },
+      {
+        internalType: "SD59x18",
+        name: "y",
+        type: "int256",
+      },
+    ],
[…]

### 2023-12-27 contract/typechain/factories/FinishContestationVote__factory.ts

@@ -1,0 +1,99 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  FinishContestationVote,
+  FinishContestationVoteInterface,
+} from "../FinishContestationVote";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IArbius",
+        name: "_arbius",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    inputs: [
+      {
+        internalType: "bytes32",
+        name: "_taskid",
+        type: "bytes32",
+      },
+      {
+        internalType: "uint32",
+        name: "_iterations",
+        type: "uint32",
+      },
+    ],
+    name: "finishVote",
+    outputs: [],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+];
+
+const _bytecode =
+  "0x608060405234801561001057600080fd5b506040516101aa3803806101aa83398101604081905261002f91610054565b600080546001600160a01b0319166001600160a01b0392909216919091179055610084565b60006020828403121561006657600080fd5b81516001600160a01b038116811461007d57600080fd5b9392505050565b610117806100936000396000f3fe6080604052348015600f57600080fd5b506004361060285760003560e01c8063974eb84114602d575b600080fd5b603c603836600460aa565b603e565b005b600054604051638b4d7b3560e01b81526004810184905263ffffffff831660248201526001600160a01b0390911690638b4d7b3590604401600060405180830381600087803b158015608f57600080fd5b505af115801560a2573d6000803e3d6000fd5b505050505050565b6000806040838503121560bc57600080fd5b82359150602083013563ffffffff8116811460d657600080fd5b80915050925092905056fea26469706673582212201b40bddd5135f7a09bfdd28b8b286458e97f6f9fc7b3ce84153fc6df37970f0d64736f6c63430008130033";
+
+type FinishContestationVoteConstructorParams =
+  | [signer?: Signer]
+  | ConstructorParameters<typeof ContractFactory>;
+
+const isSuperArgs = (
+  xs: FinishContestationVoteConstructorParams
+): xs is ConstructorParameters<typeof ContractFactory> => xs.length > 1;
+
+export class FinishContestationVote__factory extends ContractFactory {
[…]

### 2023-12-27 contract/typechain/factories/GenericTestERC20__factory.ts

@@ -1,0 +1,349 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  GenericTestERC20,
+  GenericTestERC20Interface,
+} from "../GenericTestERC20";
+
+const _abi = [
+  {
+    inputs: [],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Approval",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "from",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "to",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Transfer",
+    type: "event",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+    ],
+    name: "allowance",
+    outputs: [
+      {
+        internalType: "uint256",
+        name: "",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        internalType: "uint256",
+        name: "amount",
+        type: "uint256",
+      },
+    ],
+    name: "approve",
+    outputs: [
+      {
+        internalType: "bool",
+        name: "",
+        type: "bool",
+      },
+    ],
+    stateMutability: "nonpayable",
[…]

### 2023-12-27 contract/typechain/factories/GovernorCompatibilityBravoUpgradeable__factory.ts

@@ -1,0 +1,1224 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  GovernorCompatibilityBravoUpgradeable,
+  GovernorCompatibilityBravoUpgradeableInterface,
+} from "../GovernorCompatibilityBravoUpgradeable";
+
+const _abi = [
+  {
+    inputs: [],
+    name: "Empty",
+    type: "error",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint8",
+        name: "version",
+        type: "uint8",
+      },
+    ],
+    name: "Initialized",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
[…]

### 2023-12-27 contract/typechain/factories/GovernorSettings__factory.ts

@@ -1,0 +1,986 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  GovernorSettings,
+  GovernorSettingsInterface,
+} from "../GovernorSettings";
+
+const _abi = [
+  {
+    inputs: [],
+    name: "Empty",
+    type: "error",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalExecuted",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "oldProposalThreshold",
+        type: "uint256",
+      },
+      {
[…]

### 2023-12-27 contract/typechain/factories/GovernorTimelockControl__factory.ts

@@ -1,0 +1,1011 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  GovernorTimelockControl,
+  GovernorTimelockControlInterface,
+} from "../GovernorTimelockControl";
+
+const _abi = [
+  {
+    inputs: [],
+    name: "Empty",
+    type: "error",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalExecuted",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
[…]

### 2023-12-27 contract/typechain/factories/GovernorUpgradeable__factory.ts

@@ -1,0 +1,903 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  GovernorUpgradeable,
+  GovernorUpgradeableInterface,
+} from "../GovernorUpgradeable";
+
+const _abi = [
+  {
+    inputs: [],
+    name: "Empty",
+    type: "error",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint8",
+        name: "version",
+        type: "uint8",
+      },
+    ],
+    name: "Initialized",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
[…]

### 2023-12-27 contract/typechain/factories/GovernorVotesQuorumFractionUpgradeable__factory.ts

@@ -1,0 +1,999 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  GovernorVotesQuorumFractionUpgradeable,
+  GovernorVotesQuorumFractionUpgradeableInterface,
+} from "../GovernorVotesQuorumFractionUpgradeable";
+
+const _abi = [
+  {
+    inputs: [],
+    name: "Empty",
+    type: "error",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint8",
+        name: "version",
+        type: "uint8",
+      },
+    ],
+    name: "Initialized",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
[…]

### 2023-12-27 contract/typechain/factories/GovernorVotesQuorumFraction__factory.ts

@@ -1,0 +1,984 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  GovernorVotesQuorumFraction,
+  GovernorVotesQuorumFractionInterface,
+} from "../GovernorVotesQuorumFraction";
+
+const _abi = [
+  {
+    inputs: [],
+    name: "Empty",
+    type: "error",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalExecuted",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "oldQuorumNumerator",
[…]

### 2023-12-27 contract/typechain/factories/GovernorVotes__factory.ts

@@ -1,0 +1,900 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type { GovernorVotes, GovernorVotesInterface } from "../GovernorVotes";
+
+const _abi = [
+  {
+    inputs: [],
+    name: "Empty",
+    type: "error",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalExecuted",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "voter",
+        type: "address",
+      },
+      {
+        indexed: false,
[…]

### 2023-12-27 contract/typechain/factories/IArbius__factory.ts

@@ -1,0 +1,1754 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type { IArbius, IArbiusInterface } from "../IArbius";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "addr",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "task",
+        type: "bytes32",
+      },
+    ],
+    name: "ContestationSubmitted",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "addr",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "task",
+        type: "bytes32",
+      },
+      {
+        indexed: false,
+        internalType: "bool",
+        name: "yea",
+        type: "bool",
+      },
+    ],
+    name: "ContestationVote",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "id",
+        type: "bytes32",
+      },
+      {
+        indexed: true,
+        internalType: "uint32",
+        name: "start_idx",
+        type: "uint32",
+      },
+      {
+        indexed: false,
+        internalType: "uint32",
+        name: "end_idx",
+        type: "uint32",
+      },
+    ],
+    name: "ContestationVoteFinish",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "amount",
+        type: "uint256",
+      },
+    ],
+    name: "ExitValidatorMinUnlockTimeChanged",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "amount",
+        type: "uint256",
+      },
+    ],
+    name: "MinClaimSolutionTimeChanged",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "amount",
+        type: "uint256",
+      },
+    ],
[…]

### 2023-12-27 contract/typechain/factories/IBasicModelToken__factory.ts

@@ -1,0 +1,227 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  IBasicModelToken,
+  IBasicModelTokenInterface,
+} from "../IBasicModelToken";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Approval",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "from",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "to",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Transfer",
+    type: "event",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+    ],
+    name: "allowance",
+    outputs: [
+      {
+        internalType: "uint256",
+        name: "",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        internalType: "uint256",
+        name: "amount",
+        type: "uint256",
+      },
+    ],
+    name: "approve",
+    outputs: [
+      {
+        internalType: "bool",
+        name: "",
+        type: "bool",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "account",
+        type: "address",
+      },
+    ],
+    name: "balanceOf",
+    outputs: [
+      {
[…]

### 2023-12-27 contract/typechain/factories/IGovernorCompatibilityBravoUpgradeable__factory.ts

@@ -1,0 +1,956 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  IGovernorCompatibilityBravoUpgradeable,
+  IGovernorCompatibilityBravoUpgradeableInterface,
+} from "../IGovernorCompatibilityBravoUpgradeable";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint8",
+        name: "version",
+        type: "uint8",
+      },
+    ],
+    name: "Initialized",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalExecuted",
+    type: "event",
+  },
+  {
[…]

### 2023-12-27 contract/typechain/factories/IGovernorTimelockUpgradeable__factory.ts

@@ -1,0 +1,809 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  IGovernorTimelockUpgradeable,
+  IGovernorTimelockUpgradeableInterface,
+} from "../IGovernorTimelockUpgradeable";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint8",
+        name: "version",
+        type: "uint8",
+      },
+    ],
+    name: "Initialized",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalCanceled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "proposer",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "address[]",
+        name: "targets",
+        type: "address[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256[]",
+        name: "values",
+        type: "uint256[]",
+      },
+      {
+        indexed: false,
+        internalType: "string[]",
+        name: "signatures",
+        type: "string[]",
+      },
+      {
+        indexed: false,
+        internalType: "bytes[]",
+        name: "calldatas",
+        type: "bytes[]",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "startBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "endBlock",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "string",
+        name: "description",
+        type: "string",
+      },
+    ],
+    name: "ProposalCreated",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "proposalId",
+        type: "uint256",
+      },
+    ],
+    name: "ProposalExecuted",
+    type: "event",
+  },
+  {
[…]

### 2023-12-27 contract/typechain/factories/INonfungiblePositionManager__factory.ts

@@ -1,0 +1,1019 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { Contract, Signer, utils } from "ethers";
+import { Provider } from "@ethersproject/providers";
+import type {
+  INonfungiblePositionManager,
+  INonfungiblePositionManagerInterface,
+} from "../INonfungiblePositionManager";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "approved",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "tokenId",
+        type: "uint256",
+      },
+    ],
+    name: "Approval",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "operator",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "bool",
+        name: "approved",
+        type: "bool",
+      },
+    ],
+    name: "ApprovalForAll",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "tokenId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "recipient",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "amount0",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "amount1",
+        type: "uint256",
+      },
+    ],
+    name: "Collect",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "tokenId",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "uint128",
+        name: "liquidity",
+        type: "uint128",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "amount0",
+        type: "uint256",
+      },
+      {
+        indexed: false,
[…]

### 2023-12-27 contract/typechain/factories/L1Token__factory.ts

@@ -1,0 +1,490 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  Signer,
+  utils,
+  Contract,
+  ContractFactory,
+  Overrides,
+  BigNumberish,
+} from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type { L1Token, L1TokenInterface } from "../L1Token";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "_customGatewayAddress",
+        type: "address",
+      },
+      {
+        internalType: "address",
+        name: "_routerAddress",
+        type: "address",
+      },
+      {
+        internalType: "uint256",
+        name: "_initialSupply",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Approval",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "previousOwner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "newOwner",
+        type: "address",
+      },
+    ],
+    name: "OwnershipTransferred",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "from",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "to",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Transfer",
+    type: "event",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
[…]

### 2023-12-27 contract/typechain/factories/LookupTaskCID__factory.ts

@@ -1,0 +1,90 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type { LookupTaskCID, LookupTaskCIDInterface } from "../LookupTaskCID";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IArbius",
+        name: "_arbius",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    inputs: [
+      {
+        internalType: "bytes32",
+        name: "taskid",
+        type: "bytes32",
+      },
+    ],
+    name: "lookupTaskCID",
+    outputs: [
+      {
+        internalType: "bytes",
+        name: "",
+        type: "bytes",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+];
+
+const _bytecode =
+  "0x608060405234801561001057600080fd5b506040516103d03803806103d083398101604081905261002f91610054565b600080546001600160a01b0319166001600160a01b0392909216919091179055610084565b60006020828403121561006657600080fd5b81516001600160a01b038116811461007d57600080fd5b9392505050565b61033d806100936000396000f3fe608060405234801561001057600080fd5b506004361061002b5760003560e01c8063eecd522614610030575b600080fd5b61004361003e3660046100d7565b610059565b6040516100509190610114565b60405180910390f35b6000805460405162e579f560e81b815260048101849052606092916001600160a01b03169063e579f50090602401600060405180830381865afa1580156100a4573d6000803e3d6000fd5b505050506040513d6000823e601f3d908101601f191682016040526100cc9190810190610253565b60a001519392505050565b6000602082840312156100e957600080fd5b5035919050565b60005b8381101561010b5781810151838201526020016100f3565b50506000910152565b60208152600082518060208401526101338160408501602087016100f0565b601f01601f19169190910160400192915050565b634e487b7160e01b600052604160045260246000fd5b60405160c0810167ffffffffffffffff8111828210171561018057610180610147565b60405290565b80516001600160a01b038116811461019d57600080fd5b919050565b805167ffffffffffffffff8116811461019d57600080fd5b805160ff8116811461019d57600080fd
[…]

### 2023-12-27 contract/typechain/factories/RegisterModel__factory.ts

@@ -1,0 +1,84 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type { RegisterModel, RegisterModelInterface } from "../RegisterModel";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IArbius",
+        name: "_arbius",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    inputs: [
+      {
+        internalType: "bytes",
+        name: "_template",
+        type: "bytes",
+      },
+    ],
+    name: "registerModel",
+    outputs: [],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+];
+
+const _bytecode =
+  "0x608060405234801561001057600080fd5b506040516102d83803806102d883398101604081905261002f91610054565b600080546001600160a01b0319166001600160a01b0392909216919091179055610084565b60006020828403121561006657600080fd5b81516001600160a01b038116811461007d57600080fd5b9392505050565b610245806100936000396000f3fe608060405234801561001057600080fd5b506004361061002b5760003560e01c80630131ebac14610030575b600080fd5b61004361003e3660046100e0565b610045565b005b600080546040516327f81f7d60e11b81526001600160a01b0390911690634ff03efa9061008290309067016345785d8a0000908790600401610191565b6020604051808303816000875af11580156100a1573d6000803e3d6000fd5b505050506040513d601f19601f820116820180604052508101906100c591906101f6565b505050565b634e487b7160e01b600052604160045260246000fd5b6000602082840312156100f257600080fd5b813567ffffffffffffffff8082111561010a57600080fd5b818401915084601f83011261011e57600080fd5b813581811115610130576101306100ca565b604051601f8201601f19908116603f01168101908382118183101715610158576101586100ca565b8160405282815287602084870101111561017157600080fd5b826020860160208301376000928101602001929092525095945050505050565b60018060a01b038416815260006020848184015260606040840152835180606085015260005b818110156101d3578581018301518582016080015282016101b7565b506000608082860101526080601f19601f83011685010192505050949350505050565b60006020828403121561020857600080fd5b505191905056fea26469706673582
[…]

### 2023-12-27 contract/typechain/factories/RetractTask__factory.ts

@@ -1,0 +1,84 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type { RetractTask, RetractTaskInterface } from "../RetractTask";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IArbius",
+        name: "_arbius",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    inputs: [
+      {
+        internalType: "bytes32",
+        name: "_taskid",
+        type: "bytes32",
+      },
+    ],
+    name: "retractTask",
+    outputs: [],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+];
+
+const _bytecode =
+  "0x608060405234801561001057600080fd5b5060405161017a38038061017a83398101604081905261002f91610054565b600080546001600160a01b0319166001600160a01b0392909216919091179055610084565b60006020828403121561006657600080fd5b81516001600160a01b038116811461007d57600080fd5b9392505050565b60e8806100926000396000f3fe6080604052348015600f57600080fd5b506004361060275760003560e01c80623f9dd614602c575b600080fd5b603b6037366004609a565b603d565b005b600054604051621fceeb60e11b8152600481018390526001600160a01b0390911690623f9dd690602401600060405180830381600087803b158015608057600080fd5b505af11580156093573d6000803e3d6000fd5b5050505050565b60006020828403121560ab57600080fd5b503591905056fea264697066735822122050f887bdd76add2314160499f029d74102a5f2e458095778bd642cff036c098e64736f6c63430008130033";
+
+type RetractTaskConstructorParams =
+  | [signer?: Signer]
+  | ConstructorParameters<typeof ContractFactory>;
+
+const isSuperArgs = (
+  xs: RetractTaskConstructorParams
+): xs is ConstructorParameters<typeof ContractFactory> => xs.length > 1;
+
+export class RetractTask__factory extends ContractFactory {
+  constructor(...args: RetractTaskConstructorParams) {
+    if (isSuperArgs(args)) {
+      super(...args);
+    } else {
+      super(_abi, _bytecode, args[0]);
+    }
+  }
+
+  deploy(
+    _arbius: string,
[…]

### 2023-12-27 contract/typechain/factories/SubmitContestation__factory.ts

@@ -1,0 +1,90 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  SubmitContestation,
+  SubmitContestationInterface,
+} from "../SubmitContestation";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IArbius",
+        name: "_arbius",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    inputs: [
+      {
+        internalType: "bytes32",
+        name: "_taskid",
+        type: "bytes32",
+      },
+    ],
+    name: "submitContestation",
+    outputs: [],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+];
+
+const _bytecode =
+  "0x608060405234801561001057600080fd5b5060405161017d38038061017d83398101604081905261002f91610054565b600080546001600160a01b0319166001600160a01b0392909216919091179055610084565b60006020828403121561006657600080fd5b81516001600160a01b038116811461007d57600080fd5b9392505050565b60eb806100926000396000f3fe6080604052348015600f57600080fd5b506004361060285760003560e01c8063671f815214602d575b600080fd5b603c6038366004609d565b603e565b005b60005460405163338fc0a960e11b8152600481018390526001600160a01b039091169063671f815290602401600060405180830381600087803b158015608357600080fd5b505af11580156096573d6000803e3d6000fd5b5050505050565b60006020828403121560ae57600080fd5b503591905056fea26469706673582212205ad43764c599989c474fa571b6556de7ce4b1222ba7978fa8c6e0de1b806d01c64736f6c63430008130033";
+
+type SubmitContestationConstructorParams =
+  | [signer?: Signer]
+  | ConstructorParameters<typeof ContractFactory>;
+
+const isSuperArgs = (
+  xs: SubmitContestationConstructorParams
+): xs is ConstructorParameters<typeof ContractFactory> => xs.length > 1;
+
+export class SubmitContestation__factory extends ContractFactory {
+  constructor(...args: SubmitContestationConstructorParams) {
+    if (isSuperArgs(args)) {
+      super(...args);
+    } else {
+      super(_abi, _bytecode, args[0]);
+    }
+  }
+
+  deploy(
+    _arbius: string,
[…]

### 2023-12-27 contract/typechain/factories/SubmitTask__factory.ts

@@ -1,0 +1,118 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  Signer,
+  utils,
+  Contract,
+  ContractFactory,
+  Overrides,
+  BytesLike,
+} from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type { SubmitTask, SubmitTaskInterface } from "../SubmitTask";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IArbius",
+        name: "_arbius",
+        type: "address",
+      },
+      {
+        internalType: "contract IERC20",
+        name: "_arbiusToken",
+        type: "address",
+      },
+      {
+        internalType: "bytes32",
+        name: "_model",
+        type: "bytes32",
+      },
+      {
+        internalType: "bytes",
+        name: "_input",
+        type: "bytes",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    inputs: [],
+    name: "submitTask",
+    outputs: [],
+    stateMutability: "nonpayable",
+    type: "function",
+  },
+];
+
+const _bytecode =
+  "0x608060405234801561001057600080fd5b5060405161058538038061058583398101604081905261002f916100a8565b600080546001600160a01b038087166001600160a01b031992831617909255600180549286169290911691909117905560028290556003610070828261022b565b50505050506102ea565b6001600160a01b038116811461008f57600080fd5b50565b634e487b7160e01b600052604160045260246000fd5b600080600080608085870312156100be57600080fd5b84516100c98161007a565b809450506020808601516100dc8161007a565b6040870151606088015191955093506001600160401b038082111561010057600080fd5b818801915088601f83011261011457600080fd5b81518181111561012657610126610092565b604051601f8201601f19908116603f0116810190838211818310171561014e5761014e610092565b816040528281528b8684870101111561016657600080fd5b600093505b82841015610188578484018601518185018701529285019261016b565b600086848301015280965050505050505092959194509250565b600181811c908216806101b657607f821691505b6020821081036101d657634e487b7160e01b600052602260045260246000fd5b50919050565b601f82111561022657600081815260208120601f850160051c810160208610156102035750805b601f850160051c820191505b818110156102225782815560010161020f565b5050505b505050565b81516001600160401b03811115
[…]

### 2023-12-27 contract/typechain/factories/TimelockControllerUpgradeable__factory.ts

@@ -1,0 +1,924 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  TimelockControllerUpgradeable,
+  TimelockControllerUpgradeableInterface,
+} from "../TimelockControllerUpgradeable";
+
+const _abi = [
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "id",
+        type: "bytes32",
+      },
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "index",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "target",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "bytes",
+        name: "data",
+        type: "bytes",
+      },
+    ],
+    name: "CallExecuted",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "id",
+        type: "bytes32",
+      },
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "index",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "target",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "bytes",
+        name: "data",
+        type: "bytes",
+      },
+      {
+        indexed: false,
+        internalType: "bytes32",
+        name: "predecessor",
+        type: "bytes32",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "delay",
+        type: "uint256",
+      },
+    ],
+    name: "CallScheduled",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "id",
+        type: "bytes32",
+      },
+    ],
[…]

### 2023-12-27 contract/typechain/factories/TimelockController__factory.ts

@@ -1,0 +1,958 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  Signer,
+  utils,
+  Contract,
+  ContractFactory,
+  Overrides,
+  BigNumberish,
+} from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  TimelockController,
+  TimelockControllerInterface,
+} from "../TimelockController";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "uint256",
+        name: "minDelay",
+        type: "uint256",
+      },
+      {
+        internalType: "address[]",
+        name: "proposers",
+        type: "address[]",
+      },
+      {
+        internalType: "address[]",
+        name: "executors",
+        type: "address[]",
+      },
+      {
+        internalType: "address",
+        name: "admin",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "id",
+        type: "bytes32",
+      },
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "index",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "target",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "bytes",
+        name: "data",
+        type: "bytes",
+      },
+    ],
+    name: "CallExecuted",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "id",
+        type: "bytes32",
+      },
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "index",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "target",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "bytes",
+        name: "data",
[…]

### 2023-12-27 contract/typechain/factories/TimelockV1__factory.ts

@@ -1,0 +1,955 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import {
+  Signer,
+  utils,
+  Contract,
+  ContractFactory,
+  Overrides,
+  BigNumberish,
+} from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type { TimelockV1, TimelockV1Interface } from "../TimelockV1";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "uint256",
+        name: "minDelay",
+        type: "uint256",
+      },
+      {
+        internalType: "address[]",
+        name: "proposers",
+        type: "address[]",
+      },
+      {
+        internalType: "address[]",
+        name: "executors",
+        type: "address[]",
+      },
+      {
+        internalType: "address",
+        name: "admin",
+        type: "address",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "id",
+        type: "bytes32",
+      },
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "index",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "target",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "bytes",
+        name: "data",
+        type: "bytes",
+      },
+    ],
+    name: "CallExecuted",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "bytes32",
+        name: "id",
+        type: "bytes32",
+      },
+      {
+        indexed: true,
+        internalType: "uint256",
+        name: "index",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "address",
+        name: "target",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+      {
+        indexed: false,
+        internalType: "bytes",
+        name: "data",
+        type: "bytes",
+      },
+      {
[…]

### 2023-12-27 contract/typechain/factories/XBasicModelToken__factory.ts

@@ -1,0 +1,402 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+import { Signer, utils, Contract, ContractFactory, Overrides } from "ethers";
+import { Provider, TransactionRequest } from "@ethersproject/providers";
+import type {
+  XBasicModelToken,
+  XBasicModelTokenInterface,
+} from "../XBasicModelToken";
+
+const _abi = [
+  {
+    inputs: [
+      {
+        internalType: "contract IERC20",
+        name: "_asset",
+        type: "address",
+      },
+      {
+        internalType: "string",
+        name: "_name",
+        type: "string",
+      },
+      {
+        internalType: "string",
+        name: "_symbol",
+        type: "string",
+      },
+    ],
+    stateMutability: "nonpayable",
+    type: "constructor",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Approval",
+    type: "event",
+  },
+  {
+    anonymous: false,
+    inputs: [
+      {
+        indexed: true,
+        internalType: "address",
+        name: "from",
+        type: "address",
+      },
+      {
+        indexed: true,
+        internalType: "address",
+        name: "to",
+        type: "address",
+      },
+      {
+        indexed: false,
+        internalType: "uint256",
+        name: "value",
+        type: "uint256",
+      },
+    ],
+    name: "Transfer",
+    type: "event",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "owner",
+        type: "address",
+      },
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+    ],
+    name: "allowance",
+    outputs: [
+      {
+        internalType: "uint256",
+        name: "",
+        type: "uint256",
+      },
+    ],
+    stateMutability: "view",
+    type: "function",
+  },
+  {
+    inputs: [
+      {
+        internalType: "address",
+        name: "spender",
+        type: "address",
+      },
+      {
+        internalType: "uint256",
[…]

### 2023-12-27 contract/typechain/hardhat.d.ts

@@ -1,0 +1,753 @@
+/* Autogenerated file. Do not edit manually. */
+/* tslint:disable */
+/* eslint-disable */
+
+import { ethers } from "ethers";
+import {
+  FactoryOptions,
+  HardhatEthersHelpers as HardhatEthersHelpersBase,
+} from "@nomiclabs/hardhat-ethers/types";
+
+import * as Contracts from ".";
+
+declare module "hardhat/types/runtime" {
+  interface HardhatEthersHelpers extends HardhatEthersHelpersBase {
+    getContractFactory(
+      name: "ArbSys",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.ArbSys__factory>;
+    getContractFactory(
+      name: "OwnableUpgradeable",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.OwnableUpgradeable__factory>;
+    getContractFactory(
+      name: "IVotesUpgradeable",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.IVotesUpgradeable__factory>;
+    getContractFactory(
+      name: "Initializable",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.Initializable__factory>;
+    getContractFactory(
+      name: "ERC20Upgradeable",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.ERC20Upgradeable__factory>;
+    getContractFactory(
+      name: "ERC20PermitUpgradeable",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.ERC20PermitUpgradeable__factory>;
+    getContractFactory(
+      name: "IERC20PermitUpgradeable",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.IERC20PermitUpgradeable__factory>;
+    getContractFactory(
+      name: "ERC20VotesUpgradeable",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.ERC20VotesUpgradeable__factory>;
+    getContractFactory(
+      name: "IERC20MetadataUpgradeable",
+      signerOrOptions?: ethers.Signer | FactoryOptions
+    ): Promise<Contracts.IERC20MetadataUpgradeable__factory>;
+    getContractFactory(
+      name: "IERC20Upgradeable",
[…]

### 2023-12-27 contract/utils/config.ts

@@ -1,0 +1,64 @@
+import { config as dotenvConfig } from "dotenv";
+dotenvConfig();
+
+interface IConfig {
+  etherscan: {
+    api_key: string;
+  },
+  mainnet: {
+    provider_url: string;
+    private_key: string;
+  };
+  goerli: {
+    provider_url: string;
+    private_key: string;
+  };
+  arbgoerli: {
+    provider_url: string;
+    private_key: string;
+  };
+  nova: {
+    provider_url: string;
+    private_key: string;
+  };
+}
+
+export const getEnv = (key: string, defaultValue?: any) => {
+  const value = process.env[key];
+  if (!value) {
+    if (defaultValue === undefined || defaultValue === null) {
+      throw new Error(`Required env var ${key} not set`);
+    } else {
+      return defaultValue;
+    }
+  }
+  if (value.toLocaleLowerCase() === "false") {
+    return false;
+  }
+  if (value.toLocaleLowerCase() === "true") {
+    return true;
+  }
+  return value;
+};
+
+export const envconfig: IConfig = {
+  etherscan: {
+    api_key: getEnv("ETHERSCAN_API_KEY", ""),
+  },
+  mainnet: {
+    provider_url: getEnv("MAINNET_PROVIDER_URL", ""),
+    private_key:  getEnv("MAINNET_PRIVATE_KEY", ""),
+  },
+  goerli: {
+    provider_url: getEnv("GOERLI_PROVIDER_URL", ""),
+    private_key:  getEnv("GOERLI_PRIVATE_KEY", ""),
+  },
+  arbgoerli: {
+    provider_url: getEnv("ARBGOERLI_PROVIDER_URL", ""),
+    private_key:  getEnv("ARBGOERLI_PRIVATE_KEY", ""),
+  },
+  nova: {
+    provider_url: getEnv("NOVA_PROVIDER_URL", ""),
+    private_key:  getEnv("NOVA_PRIVATE_KEY", ""),
+  },
+};

### 2023-12-27 miner/src/blockchain.ts

@@ -1,0 +1,73 @@
+import { ethers, Contract, Wallet, BigNumber } from 'ethers';
+
+import { c } from './mc';
+import Config from './config.json';
+import { expretry } from './utils';
+
+import EngineArtifact from './artifacts/EngineV1.sol/EngineV1.json';
+import BaseTokenArtifact from './artifacts/BaseTokenV1.sol/BaseTokenV1.json';
+import GovernorArtifact from './artifacts/GovernorV1.sol/GovernorV1.json';
+import DelegatedValidator from './artifacts/DelegatedValidatorV1.sol/DelegatedValidatorV1.json';
+import ArbSysArtifact from './artifacts/ArbSys.sol/ArbSys.json';
+
+const ARBSYS_ADDR = '0x0000000000000000000000000000000000000064';
+
+let wallet:   Wallet;
+let arbius:   Contract;
+let token:    Contract;
+let governor: Contract;
+let solver:   Contract; // this could be be either arbius or delegated validator
+let arbsys:   Contract;
+
+export async function initializeBlockchain() {
+  const provider = new ethers.providers.JsonRpcProvider(c.blockchain.rpc_url!);
+  wallet = new Wallet(c.blockchain.private_key, provider);
+
+  arbius   = new Contract(Config.engineAddress,    EngineArtifact.abi,    wallet);
+  token    = new Contract(Config.baseTokenAddress, BaseTokenArtifact.abi, wallet);
+  governor = new Contract(Config.governorAddress,  GovernorArtifact.abi,  wallet);
+  arbsys   = new Contract(ARBSYS_ADDR,             ArbSysArtifact.abi,    wallet);
+
+  if (! c.blockchain.use_delegated_validator) {
+    solver = new Contract(Config.engineAddress,    EngineArtifact.abi,    wallet);
+  } else {
+    solver = new Contract(c.blockchain.delegated_validator_address, DelegatedValidator.abi, wallet);
+  }
+}
+
+// TODO check if we are on nova network, if so use this, otherwise block.number
+export async function getBlockNumber() {
+  const abn = await expretry(async () => await arbsys.arbBlockNumber());
+  return abn;
+}
+
+export async function getValidatorStaked(): Promise<BigNumber> {
+  const staked = await expretry(async () => {
+    if (c.blockchain.use_delegated_validator) {
+      const s = (await arbius.validators(c.blockchain.delegated_validator_address)).staked;
+      return s;
+    }
+
[…]

### 2023-12-27 miner/src/log.ts

@@ -1,0 +1,29 @@
+import * as fs from 'fs';
+import { Logger, ILogObj } from "tslog";
+
+let log: Logger<ILogObj>;
+
+export function initializeLogger(log_path: string|null) {
+  log = new Logger();
+
+  if (log_path != null) {
+    log.attachTransport((lobj) => {
+      let p = '[fileNameWithLine undefined]';
+      if (lobj._meta.path && lobj._meta.path.fileNameWithLine) {
+        p = lobj._meta.path.fileNameWithLine;
+      }
+
+      let m = []
+      for (let i=0; i<10; ++i) {
+        if (lobj.hasOwnProperty(i.toString())) {
+          m.push(lobj[i]);
+        }
+      }
+
+      const l = `${lobj._meta.date.getTime()} ${lobj._meta.logLevelName} ${p} ${m.join('\t')}\n`;
+      fs.appendFileSync(log_path, l);
+    });
+  }
+}
+
+export { log };

### 2023-12-27 miner/src/rpc.ts

@@ -1,0 +1,104 @@
+import { c } from './mc';
+import { log } from './log';
+import { dbQueueJob, dbGetJobs, dbDeleteJob } from './db';
+
+import bodyParser from 'body-parser';
+import express, { Express, Request, Response } from 'express';
+
+const app: Express = express();
+app.use(bodyParser.json());
+
+app.get('/', (req: Request, res: Response) => {
+  res.send('Arbius Miner RPC');
+});
+
+app.post('/api/jobs/queue', async (req: Request, res: Response) => {
+  try {
+    const rfields = [
+      ['method', 'string'],
+      ['priority', 'number'],
+      ['waituntil', 'number'],
+      ['concurrent', 'boolean'],
+      ['data', 'object'],
+    ];
+    rfields.forEach(([field, etype]) => {
+      if (typeof req.body[field] === 'undefined') {
+        throw new Error(`missing required field (${field})`);
+      }
+      if (typeof req.body[field] !== etype) {
+        throw new Error(`expected (${field}) to be type (${etype}), got (${typeof req.body[field]})`);
+      }
+    });
+
+    await dbQueueJob({
+      method:     req.body.method,
+      priority:   req.body.priority,
+      waituntil:  req.body.waituntil,
+      concurrent: req.body.concurrent,
+      data:       req.body.data,
+    });
+
+    return res.json({ status: 'ok' });
+  } catch (e: any) {
+    return res.json({ status: 'fail', e: e.toString() });
+  }
+});
+
+app.post('/api/jobs/get', async (req: Request, res: Response) => {
+  try {
+    let limit = 100_000;
+
+    if (typeof req.body.limit !== 'undefined') {
+      const parsedLimit = parseInt(req.body.limit);
+      if (isNaN(parsedLimit)) {
+        throw new Error('limit NaN');
+      }
+
+      limit = parsedLimit;
+    }
+
+    const jobs = await dbGetJobs(limit);
+    return res.json({ status: 'ok', jobs });
+  } catch (e: any) {
+    return res.json({ status: 'fail', e: e.toString() });
+  }
+});
+
+app.post('/api/jobs/delete', async (req: Request, res: Response) => {
+  try {
+    const id = parseInt(req.body.id);
+    if (isNaN(id)) {
+      throw new Error('id NaN');
+    }
+    await dbDeleteJob(req.body.id);
+    return res.json({ status: 'ok' });
+  } catch (e: any) {
+    console.log(e);
[…]

### 2023-12-27 miner/src/scripts/pinata_unpin_old_files.ts

@@ -1,0 +1,69 @@
+/*
+import dotenv from "dotenv"
+dotenv.config();
+
+import axios from 'axios';
+import {
+  sleep,
+} from './utils';
+
+if (typeof process.env.REPLICATE_API_TOKEN === 'undefined' ||
+    typeof process.env.PINATA_JWT === 'undefined'
+) {
+  console.error('Ensure REPLICATE_API_TOKEN and PINATA_JWT are set in .env');
+  process.exit(1);
+}
+
+async function getOldPinnedFiles() {
+  const HOURS = 2;
+  const pinStart = (new Date('05 October 2011 14:48 UTC')).toISOString();
+  const pinEnd = (new Date((+(new Date()))-(1000*60*60*HOURS))).toISOString();
+
+  const res = await axios({
+    method: 'get',
+    url: `https://api.pinata.cloud/data/pinList?status=pinned&pinStart=${pinStart}&pinEnd=${pinEnd}`,
+    headers: { 
+      'Authorization': `Bearer ${process.env.PINATA_JWT}`
+    },
+  });
+  
+  return res.data;
+}
+
+async function unpinFile(cid: string) {
+  const res = await axios({
+    method: 'delete',
+    url: `https://api.pinata.cloud/pinning/unpin/${cid}`,
+    headers: {
+      'Authorization': `Bearer ${process.env.PINATA_JWT}`
+    }
+  });
+  console.log(res.data);
+}
+
+
+async function main() {
+  while (true) {
+    try {
+      const old = await getOldPinnedFiles();
+      if (old.count === 0) {
+        console.log('no old files found, sleeping for a minute');
+        await sleep(60_000);
+        continue;
+      }
+  
+      console.log(`found ${old.count} old pinned files`);
+    
+      for (let row of old.rows) {
+        const cid = row.ipfs_pin_hash;
+        console.log(`unpinning cid ${cid}`);
+        await unpinFile(cid);
+      }
+    } catch (e) {
+      console.error(JSON.stringify(e));
+    }
+  }
+}
+
+main();
+*/

### 2023-12-27 miner/src/start.ts

@@ -1,0 +1,59 @@
+import * as child_process from 'child_process';
+import * as fs from 'fs';
+import { initializeLogger, log } from './log';
+import { c, initializeMiningConfig } from './mc';
+import { initializeDatabase } from './db';
+import { initializeML } from './ml';
+import { initializeBlockchain, wallet } from './blockchain';
+import { initializeRPC } from './rpc';
+import { main } from './index';
+
+async function start(configPath: string) {
+  try {
+    const mconf = JSON.parse(fs.readFileSync(configPath, 'utf8'));
+    initializeMiningConfig(mconf);
+  } catch (e) {
+    console.error(`unable to parse ${configPath}`);
+    process.exit(1);
+  }
+  
+  if (c.evilmode) {
+    for (let i=0; i<20; ++i) {
+      log.warn('YOU HAVE EVIL MODE ENABLED, YOU WILL BE SLASHED');
+      log.warn('KILL YOUR MINER IMMEDIATELY IF NOT ON TESTNET');
+    }
+  }
+  
+  initializeLogger(c.log_path);
+
+  try {
+    const rev = child_process.execSync('git rev-parse HEAD').toString().trim();
+    log.info(`Arbius Miner ${rev.substring(0, 8)} starting`);
+  } catch (e) {
+    log.warn('Could not run "git rev-parse HEAD" do you have git in PATH?');
+  }
+
+  log.debug(`Logging to ${c.log_path}`);
+  
+  await initializeDatabase(c);
+  log.debug(`Database loaded from ${c.db_path}`);
+
+  await initializeML(c);
+  log.debug(`ML initialized`);
+  
+  await initializeBlockchain();
+  log.debug(`Loaded wallet (${wallet.address})`);
+
+  await initializeRPC();
+  log.debug(`RPC initialized`);
+
+  await main();
+  process.exit(0);
+}
+
+if (process.argv.length < 3) {
+  console.error('usage: yarn start MiningConfig.json');
+  process.exit(1);
+}
+
+start(process.argv[2]);

### 2023-12-27 miner/src/types.ts

@@ -1,0 +1,204 @@
+import { BigNumber } from 'ethers';
+
+export interface MiningConfig {
+  log_path: string|null;
+  db_path: string;
+  stake_buffer_percent: number;
+  stake_buffer_topup_percent: number;
+  evilmode: boolean;
+
+  blockchain: {
+    private_key: string;
+    rpc_url: string;
+    use_delegated_validator: boolean;
+    delegated_validator_address: string;
+  };
+
+  rpc: {
+    host: string;
+    port: number;
+  };
+
+  automine: {
+    enabled: boolean;
+    delay: number;
+    version: number;
+    model: string;
+    fee: string; // string for bignum
+    input: {
+      prompt: string;
+    };
+  };
+
+  ml: {
+    strategy: "cog"|"replicate";
+    cog: {
+    };
+    replicate: {
+      api_token: string;
+    };
+  };
+
+  ipfs: {
+    strategy: "http_client"|"pinata";
+    http_client: {
+      url: string;
+    }
+    pinata: {
+      jwt: string;
+    };
+  }
+}
+
+export interface Task {
+  model: string;
+  fee: BigNumber;
+  owner: string;
+  blocktime: BigNumber;
+  version: number;
+  cid: string;
+}
+
+export interface Solution {
+  validator: string;
+  blocktime: BigNumber;
+  claimed: boolean;
+  cid: string;
+}
+
+export interface Job {
+  priority: number;
+  waituntil: number;
+  concurrent: boolean;
+  method: string;
+  data: string;
+}
+
+export interface MiningFilter {
+  minfee:  BigNumber;
+  mintime: number;
+  owner?:  string;
+}
+
+export interface Model {
+  // modelid
+  id: string;
+  // which template to use for generating response
+  template: any;
+  // does model generate mining rewards
+  mineable: boolean;
+  // these iterated over each task to check if it fits filter
+  filters: MiningFilter[];
+
+  // function that uses ml strategy and returns list of files
+  getfiles: (m: Model, taskid: string, input: any) => Promise<string[]>;
+
+  // function that mines and returns cid
+  getcid: (MiningConfig: any, m: Model, taskid: string, input: any) => Promise<string|null>;
+}
+
+export interface DBTask {
+  id: string;
+  modelid: string;
+  fee: string;
+  address: string;
+  blocktime: string;
+  version: number;
+  cid: string;
+  retracted: boolean;
+};
+
[…]

### 2023-12-27 miner/src/utils.ts

@@ -1,0 +1,49 @@
+import { ethers, BigNumber } from 'ethers';
+import { log } from './log';
+
+
+export async function sleep(ms: number): Promise<void> {
+  return new Promise((resolve, reject) => setTimeout(resolve, ms));
+}
+
+export function now(): number {
+  return Math.floor((+new Date)/1000);
+}
+
+// torch.generator().manual_seed allows 2^64-1
+// but for easy interop with existing tooling we reduce this
+export function taskid2Seed(taskid: string): number {
+  // Number.MAX_SAFE_INT-15 to keep things easy
+  const m = 0x1FFFFFFFFFFFF0;
+  return BigNumber.from(taskid).mod(m).toNumber();
+}
+
+export async function expretry<T>(
+  fn: () => Promise<T>,
+  tries: number = 10,
+  base: number = 1.5,
+): Promise<T|null> {
+  for (let retry=0; retry<tries; ++retry) {
+    try {
+      return await fn();
+    } catch (e) {
+      const seconds = base**retry;
+      log.warn(`retry request failed, retrying in ${seconds}`);
+      log.debug(JSON.stringify(e));
+      await sleep(1000 * seconds);
+    }
+  }
+  log.error(`retry request failed ${tries} times`);
+
+  return null;
+}
+
+// expects hex values
+export function generateCommitment(address: string, taskid: string, cid: string): string {
+  return ethers.utils.keccak256(
+    ethers.utils.defaultAbiCoder.encode(
+      ['address', 'bytes32', 'bytes'],
+      [address, taskid, cid]
+    )
+  );
+}

### 2023-12-27 miner/test/ipfs.test.ts

@@ -1,0 +1,136 @@
+import dotenv from 'dotenv';
+dotenv.config();
+import { expect } from 'chai';
+import * as fs from 'fs';
+import { base58 } from '@scure/base';
+import { pinFileToIPFS, pinFilesToIPFS } from '../src/ipfs';
+import { c, initializeMiningConfig } from '../src/mc';
+import { MiningConfig } from '../src/types';
+
+
+const mconf = {
+  "log_path": null,
+  "db_path": ":memory:",
+  "stake_buffer_percent": 20,
+  "evilmode": false,
+
+  "blockchain": {
+    "private_key": "",
+    "rpc_url": "https://nova.arbitrum.io/rpc"
+  },
+
+  "automine": {
+    "enabled": false,
+    "delay": 60,
+    "version": 0,
+    "model": "0x7cb00aefb0992612b38464630c161fa7f36d727f0a52bcf926e7d8a361af86c7",
+    "fee": "0",
+    "input": {
+      "prompt": ""
+    }
+  },
+  "ml": {
+    "strategy": "replicate",
+    "replicate": {
+      "api_token": process.env.TEST_REPLICATE_API_TOKEN!,
+    },
+    "cog": {
+    }
+  },
+  "ipfs": {
+    "strategy": "pinata",
+    "pinata": {
+      "jwt": process.env.TEST_PINATA_JWT!,
+    },
+    "http_client": {
+      "url": "http:/127.0.0.1:5001",
+    },
+  }
+};
+
+
+describe('IPFS', function() {
+  this.timeout(10000); 
+
+  it('pin files by content (pinata)', async () => {
+    mconf.ipfs.strategy = 'pinata';
+    initializeMiningConfig(mconf as MiningConfig);
+
+    const paths = [
+      `out-1.png`,
+      `ipfs_a.bin`,
+      `ipfs_b.bin`,
+      `ipfs_c.bin`,
+      `ipfs_d.bin`,
+    ];
+
+    const cid = await pinFilesToIPFS(c, 'taskidtest', paths);
+    console.log(cid);
+  });
+
+  it('pin files by content (http_client)', async () => {
+    mconf.ipfs.strategy = 'http_client';
+    initializeMiningConfig(mconf as MiningConfig);
+
+    const paths = [
+      `out-1.png`,
[…]

### 2023-12-27 setup_local.sh

@@ -1,0 +1,23 @@
+#!/bin/bash
+
+# script to initialize local blockchain for testing
+# have `npx hardhat node` running
+
+
+set -e
+
+source ~/.nvm/nvm.sh
+
+cd contract
+nvm use
+
+# do this after nvm setup to skip printing all of that
+set -x
+
+npx hardhat --network localhost run scripts/001-deploy.ts
+
+# delegate voting to self
+npx hardhat --network localhost governance:delegate --address 0xf39Fd6e51aad88F6F4ce6aB8827279cffFb92266
+
+# deploy a delegated validator
+npx hardhat --network localhost validator:deploy-delegation 0x7d0e9c2d39fba3c92e7473b203c02414a2d38f565873e7aa5715d5262918f518

### 2023-12-27 website/nightwind.d.ts

@@ -1,0 +1,54 @@
+declare module 'nightwind/helper' {
+
+/**
+ * To initialize nightwind, add the following script tag to the head element of your pages.
+ *
+ * ```
+ * import nightwind from "nightwind/helper"
+ *
+ * export default function Layout() {
+ *   return (
+ *     <>
+ *       <Head>
+ *         <script dangerouslySetInnerHTML={{ __html: nightwind.init() }} />
+ *       </Head>
+ *       // ...
+ *     </>
+ *   )
+ * }
+ * ```
+ */
+export declare function init(): string;
+/**
+ * Similarly, you can use the toggle function to switch between dark and light mode.
+ * ```
+ * import nightwind from "nightwind/helper"
+ *
+ * export default function Navbar() {
+ *   return (
+ *     // ...
+ *     <button onClick={() => nightwind.toggle()}></button>
+ *     // ...
+ *   )
+ * }
+ * ```
+ */
+export declare function toggle(): void;
+/**
+ * You can use the enable function to specifically switch between dark and light mode.
+ * ```
+ * import nightwind from "nightwind/helper"
+ *
+ * export default function Navbar() {
+ *   return (
+ *     // ...
+ *     <button onClick={() => nightwind.enable(true)}></button>
+ *     // ...
+ *   )
+ * }
+ * ```
+ */
+export declare function enable(dark: boolean): void;
+
+export declare function beforeTransition(): void;
+}

### 2023-12-27 website/src/models.ts

@@ -1,0 +1,37 @@
+import { ethers } from 'ethers'
+import Config from '@/config.json';
+
+
+// import AnythingV3Template from '@/templates/anythingv3.json';
+import ZeroscopeTemplate from '@/templates/zeroscopev2xl.json';
+import Kandinsky2Template from '@/templates/kandinsky2.json';
+
+
+export const models = [
+  [Config.models.kandinsky2.id, 'Kandinsky2'],
+//  [Config.models.anythingv3.id, 'AnythingV3'],
+  [Config.models.zeroscopev2xl.id, 'Zeroscope V2 XL'],
+];
+
+export function getModelTemplate(modelid: string): any {
+  switch (modelid) {
+    //case Config.models.anythingv3.id:
+    //  return AnythingV3Template;
+    case Config.models.zeroscopev2xl.id:
+      return ZeroscopeTemplate;
+    case Config.models.kandinsky2.id:
+      return Kandinsky2Template;
+  }
+
+  return null;
+}
+
+export function getModelFee(modelid: string): any {
+  for (const [k, v] of Object.entries(Config.models)) { 
+    if (modelid === v.id) {
+      return ethers.BigNumber.from(v.params.fee);
+    }
+  }
+
+  return ethers.constants.Zero;
+}

### 2023-12-27 website/src/pages/api/imagecache.ts

@@ -1,0 +1,32 @@
+import * as fs from 'fs';
+import axios from 'axios';
+import type { NextApiRequest, NextApiResponse } from 'next'
+
+export default async function handler(req: NextApiRequest, res: NextApiResponse) {
+  if (req.method !== 'GET') {
+    res.status(405).json({ msg: 'method not allowed' });
+    return;
+  }
+
+  if (typeof req.query.url !== 'string') {
+    res.status(400).json({ msg: 'query missing url' });
+    return;
+  }
+
+  const decodedUri = decodeURIComponent(req.query.url);
+
+  res.setHeader('Cache-Control', 's-maxage=604800');
+  res.setHeader('Content-Type', 'image/jpg');
+
+  try {
+    const response = await axios.get(decodedUri, {
+      timeout: 10_000,
+      responseType: 'arraybuffer',
+    });
+
+    res.status(200).send(response.data);
+  } catch (e) {
+    console.log('IMAGECACHE ERROR', JSON.stringify(e));
+    res.status(404);
+  }
+}

### 2023-12-27 website/src/utils.ts

@@ -1,0 +1,40 @@
+import { base58 } from '@scure/base';
+import { ethers } from 'ethers'
+
+export function secondsToDhms(seconds: number) {
+  const d = Math.floor(seconds / (3600*24));
+  const h = Math.floor(seconds % (3600*24) / 3600);
+  const m = Math.floor(seconds % 3600 / 60);
+  const s = Math.floor(seconds % 60);
+  
+  const dDisplay = d > 0 ? d + (d == 1 ? " day" : " days") : "";
+  const hDisplay = h > 0 ? h + (h == 1 ? " hour" : " hours") : "";
+  const mDisplay = m > 0 ? m + (m == 1 ? " minute" : " minutes") : "";
+  const sDisplay = s > 0 ? s + (s == 1 ? " second" : " seconds") : "";
+
+  if (d > 0) return `${dDisplay}, ${hDisplay}`;
+  if (h > 0) return `${hDisplay}, ${mDisplay}`;
+  if (m > 0) return `${mDisplay}, ${sDisplay}`;
+
+  return sDisplay;
+}
+
+export function cidify(cid: string): string {
+  if (! cid) {
+    return '';
+  }
+  return base58.encode(ethers.utils.arrayify(cid));
+}
+
+export function formatBalance(b: ethers.BigNumber, m: number = 1e14): string {
+    if (! b) {
+      return '';
+    }
+
+    const remainder = b.mod(m);
+    return ethers.utils.formatEther(b.sub(remainder));
+}
+
+export function sleep(ms: number) {
+  return new Promise((res, rej) => setTimeout(res, ms));
+}

### 2024-01-27 paper/paper.tex
paper update

@@
 
-AIUS has 1 million max supply, with a time based target total supply of $1000000(1-{0.5^{y})}$ where y is year.
-After 1 year, there should be approximately 500k tokens minted, and after 2 years approximately 750k tokens minted.
+AIUS has 1 million max supply with both exponentially decaying inflation driven by mining, as well as various vesting schedules to ensure long term sustainability of the protocol.
+
+The distribution is as follows:
+
+\begin{itemize}
+    \item 1\% Initial Liquidity
+    \item 9\% Liquidity Incentives (\approx 4 year vesting)
+    \item 10\% DAO (\approx 4 year vesting)
+    \item 10\% Team (4 year vesting)
+    \item 10\% Private sale (2 year vesting)
+    \item 60\% Mining (\approx 7 year emission schedule)
+\end{itemize}
+
+\subsection{DAO}
+
+10\% of all tokens are sent to the Arbius DAO treasury.
+These tokens are to be utilized by the DAO for future development and promotion of the protocol.
+The soft target is to have DAO funds cover at least 4 years of development, with the goal of having the DAO be self-sustaining by the end of the 4 year period.
+
+\subsection{Liquidity Incentives}
+
+Initially 10k AIUS(1\% of total supply) and \$30k of ETH will be used to create a Uniswap pool.
+The remaining 9\% will be used to incentivize liquidity providers.
+Users will be able to stake and bond liquidity in order to receive AIUS rewards.
+The 9\% will be distributed over 4 years, with the first year having the highest rewards.
+Of the 9\%(90k AIUS), rewards are expected to be deployed between LP Rewards / Bonds as follows:
+
+\begin{itemize}
+    \item Year 1: 20\%/20\% (36k AIUS)
+    \item Year 2: 15\%/15\% (27k AIUS)
+    \item Year 3: 10\%/10\% (18k AIUS)
+    \item Year 4: 5\%/5\% (9k AIUS)
+\end{itemize}
+
+The proportion of rewards between LP Incentivization and Bonding may be adjusted by the DAO or team to maximize liquidity and stability of the token.
+
+\subsection{Mining}
+
+Mining is covered with a time based target total supply of $600000(1-{0.5^{y})}$ where y is year.
+After 1 year, there should be approximately 300k tokens minted, and after 2 years approximately 450k tokens minted.
 After 7 years approximately 99\% of tokens should be minted.
-
-\begin{figure}[H]
-\includegraphics[width=8cm]{totalsupply}
-\centering
-\end{figure}
 
@@
 
-10\% of all newly minted tokens, and 10\% of task fees are sent to the treasury.
-An additional 10\% of all newly minted tokens will be dripped to liquidity providers to incentivize AIUS/ETH liquidity; governance can adjust this percentage.
-
-There are at least 4 ways for participants to earn with the AIUS protocol:
+There are at least 4 ways for participants to earn with the Arbius protocol:
 
@@
     \item Solve tasks and earn task rewards and fees
-    \item Stake AIUS and delegate to solver for portion of task rewards
     \item Stake AIUS/ETH LP tokens for portion of newly created AIUS
+    \item Bond AIUS/ETH LP tokens for portion of newly created AIUS
 \end{enumerate}

### 2024-02-04 paper/paper.tex
paper updates

@@
 \usepackage{hyperref}
-\hypersetup{
-    colorlinks,
-    linkcolor={blue},
-    citecolor={blue},
-    urlcolor={blue}
-}
+\hypersetup{colorlinks, linkcolor={blue}, citecolor={blue}, urlcolor={blue}}
 \usepackage[natbib=true, style=numeric,sorting=none]{biblatex}
@@
 \author{Kasumi}
-\date{October 2023}
+\date{January 2023}
 
@@
 
-A peer-to-peer hybrid proof-of-work/proof-of-stake token (AIUS) based on reproducible computation allows anyone in the world to serve and request AI models without requiring a trusted third party.
-Such a system is capable of producing results such as Stable Diffusion \cite{stablediffusion} image generation with low latency overhead and competitive fees to centralized providers.
-Models are able to accrue fees into smart contracts, providing a decentralized a way for creators to generate income from utility and usage of their work.
+The Arbius token (AIUS) is mineable and based on a new Proof-of-AI-Compute algorithm.
+It incentivizes reproducible computation allowing anyone in the world to serve and request AI models without requiring a trusted third party.
+Such a system is capable of producing results such as Stable Diffusion\cite{stablediffusion} image generation with low latency overhead and competitive fees to centralized providers.
+Models are able to accrue fees into smart contracts, providing a decentralized way for creators to generate income from utility and usage of their work.
 Censoring models is economically infeasible, allowing for truly unstoppable AI systems.
@@
 
-To create a task a user prepares input data for the task and submits a transaction containing the model and the input data.
-along with an optional fee (paid in AIUS) to the blockchain.
+To create a task a user prepares input data for the task and submits a transaction containing the model and the input data, along with an optional fee (paid in AIUS) to the blockchain.
 The IPFS\cite{benet2014ipfs} Content Identifier (CID) is calculated by a smart contract and stored, miners may automatically mirror the input data.
@@
 \begin{enumerate}
-    \item User formats a task request
-    \item User broadcasts a transaction calling createTask and attaches a fee
-    \item Contract calculates CID of input data and stores it
-    \item Solvers that are scanning for tasks download the request data
-    \item Solvers run associated model using user's input and a seed derived from the task and system state
-    \item Solvers pin model response to IPFS and broadcast a commitment transaction referencing the task and response hash
+    \item User formats a task request.
+    \item User broadcasts a transaction calling createTask and attaches a fee.
+    \item Contract calculates CID of input data and stores it.
+    \item Solvers that are scanning for tasks download the request data.
+    \item Solvers run associated model using user's input and a seed derived from the task and system state.
+    \item Solvers pin model response to IPFS and broadcast a commitment transaction referencing the task and response hash.
     \item Solvers broadcast a solution referencing the task, commitment, and solution data. The first solution proposed wins.
@@
 \begin{enumerate}
-    \item Solver contests a solution referencing its task id
-    \item Other solvers are scanning for new contestations, and choose to verify the task was completed accurately by the solution submitter
+    \item Solver contests a solution referencing its task id.
+    \item Other solvers are scanning for new contestations, and choose to verify the task was completed accurately by the solution submitter.
     \item Solvers vote over a period of time on whether the contestation was valid.
@@
 
-More details about contestations can be found in \ref{contestation}.
+More details about contestations can be found in~\ref{contestation}.
 
-\subsection{Task Reward} \label{taskreward}
+\subsection{Task Reward}\label{taskreward}
 
@@
 
-Task rewards works similarly to how difficulty in Bitcoin \cite{bitcoin} adjusts the work required to mine a block to target an emission schedule, we adjust the reward amount per task to target our emission schedule(\ref{tokenomics} for schedule).
+Task rewards works similarly to how difficulty in Bitcoin\cite{bitcoin} adjusts the work required to mine a block to target an emission schedule, we adjust the reward amount per task to target our emission schedule~(\ref{tokenomics} for schedule).
 
@@
 Machine learning models may be registered permissionlessly.
-Each model references a docker container which follows a standard Cog \cite{cog} interface for interacting with it.
+Each model references a docker container which follows a standard Cog\cite{cog} interface for interacting with it.
 This allows great flexibility in the types of models that can be run, and importantly, allows each run to be reproducible.
@@
 This allows models to operate as DAOs, with their own token dynamics decided by their respective teams.
-A simple case would be to have the fees accrued be distributed pro-rata to holders of the DAO.
+A simple case would be to have the fees accrued be distributed pro-rata to holders of the DAO\@.
 
@@
 
-Once complete, solvers upload the result to IPFS and save the CID.
+Once complete, solvers upload the result to IPFS and save the CID\@.
 Then they submit a commitment containing a hash of their solution in order to prevent others from stealing their work by watching the mempool (or sequencer queue or similar).
-Once the commitment is confirmed, they can safely broadcast their transaction referencing the task and their solution CID.
+Once the commitment is confirmed, they can safely broadcast their transaction referencing the task and their solution CID\@.
 The task is now locked from others submitting.
 
-\subsection{Contestation} \label{contestation}
+\subsection{Contestation}\label{contestation}
 
@@
 
-\section{Tokenomics} \label{tokenomics}
+\newpage
+
+\section{Tokenomics}\label{tokenomics}
 
@@
 \begin{itemize}
-    \item 1\% Initial Liquidity
-    \item 9\% Liquidity Incentives (\approx 4 year vesting)
-    \item 10\% DAO (\approx 4 year vesting)
+    \item 1\% Initial DEX Liquidity
+    \item 9\% DEX Liquidity Provider Incentives ($\approx4$ year vesting)
+    \item 10\% DAO ($\approx4$ year vesting)
     \item 10\% Team (4 year vesting)
     \item 10\% Private sale (2 year vesting)
-    \item 60\% Mining (\approx 7 year emission schedule)
+    \item 60\% Mining ($\approx7$ year emission schedule)
 \end{itemize}
 
+\begin{figure}[h]
+\caption{Total supply curve}
+\centering
+\includegraphics[width=0.9\textwidth]{combined}
+\end{figure}
+
+\begin{figure}[h]
+    \caption{Supply curve components}
+\centering
+\includegraphics[width=1.0\textwidth]{separate}
+\end{figure}
+
+\newpage
 \subsection{DAO}
 
-10\% of all tokens are sent to the Arbius DAO treasury.
+10\% of all tokens as well as 10\% of task fees are sent to the Arbius DAO treasury.
 These tokens are to be utilized by the DAO for future development and promotion of the protocol.
@@
 
-Initially 10k AIUS(1\% of total supply) and \$30k of ETH will be used to create a Uniswap pool.
+Initially 10k AIUS (1\% of total supply) and \$30k of ETH will be used to create a Uniswap pool.
+This equates to \$3 per token, \$3m~FDV, the same valuation as provided to the private sale investors.
 The remaining 9\% will be used to incentivize liquidity providers.
@@
 
-Mining is covered with a time based target total supply of $600000(1-{0.5^{y})}$ where y is year.
-After 1 year, there should be approximately 300k tokens minted, and after 2 years approximately 450k tokens minted.
+Mining is covered with a time based target total supply of $600000(1-{0.5^{y}})$ where y is year.
+After 1 year, there should be approximately 300k tokens minted via mining, and after 2 years approximately 450k tokens minted.
 After 7 years approximately 99\% of tokens should be minted.
 
-The real emission rate (recall \ref{taskreward}) will be slightly faster than the target emission rate, due to the variable task reward.
+The real emission rate (recall~\ref{taskreward}) will be slightly faster than the target emission rate, due to the variable task reward.
 However, it is unlikely to be much more than 10\% faster due to the exponential falloff of task rewards.
 10\% greater total supply than expected total supply by time results in a 1024-fold reduction of task rewards.
+
+\subsection{Economic Incentive}
 
@@
 
-All contracts and treasury are owned by a governor contract which implements Bravo \cite{bravo} style voting.
+All contracts and treasury are owned by a governor contract which implements Bravo\cite{bravo} style voting.
 An initial quorum requirement of 4\%, a 1 day voting delay for proposals, and 1 week voting period are set as the initial parameters.
@@
 
-We choose Arbitrum Nova \cite{arbitrumnitro}.
+We choose Arbitrum Nova\cite{arbitrumnitro}.
 Arbitrum Nova is a Layer 2 optimistic rollup built on top of Ethereum.
@@
 
-\printbibliography
+\printbibliography{}
 
@@
 
-We already see the early stages of autonomous AI with technologies such as BabyAGI and Auto-GPT.
+We already see the early stages of autonomous AI with technologies such as Auto-GPT\@.
 While it is impossible to predict how fast these will evolve and become capable of living independently of humans, it is inevitable, and quickly approaching.
